---
title: "2018.03_AM_HFO_2mo_MQY_v1"
author: "Mikaela Nordborg"
date: "21/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#For model fitting, evaluation & extraction of results
library(readr)
library(tidyr)
library(dplyr)
require(tidyverse)
library(brms)
library(bayesnec) #install from CRAN in the first instance, for intermediate updates use devtools::install_github("open-AIMS/bayesnec")
library(beepr)

inv.log10 <- function(x){10^x}


#For plotting
library(ggplot2)
library(scales)
library(tidybayes)

#For creating layouts & exports
library(ggpubr) #devtools::install_github("kassambara/ggpubr")
```

# Background

Maximum quantum yield (MQY) of young Acropora millepora corals (2 months post-settlement) exposed to the water accommodated fractions (WAF) of heavy fuel oil in the presence or absence of ultraviolet radiation (UV).

Column headings used:

  date                        = date of assessment/imaging
  exp_time                    = exposure time (days)
  light                       = light treatment corals were exposed under; visible light in the absence (PAR) or presence (UVR) of UV radiation
  nom.x                       = nominal treatment concentration (% WAF)
  raw.x                       = time-averaged, measured treatment concentration (ug TAH/L)
  rep                         = replicate chamber.ID for the treatment combination (1-7)
  chamber.ID                     = exposure chamber.ID used (1-79)
  tile.ID                     = tile number (1-249)
  org.ID                      = identifier for individual corals within a replicate
  area_image_ID               = file identifier for the image file used to obtain live tissue area measurements
  IPAM_image_ID               = file identifier for MAXI PAM images used to measure maximum quantum yield
  yield                       = maximum quantum yield (Fv/Fm) recorded (>0)
  comments                    = comments relating to individual data points
  use_in_model                = specifies which data points should be included in statistical analysis
  reason_for_exclusion        = specifies the reason for exclusion form statistical analysis (f applicable)
  use_in_plot                 = specifies whether data should be used in results graphics or not
  reason_for_exclusion_plot   = specifies why data point should not be included in result graphics
  
 



# Import and prepare data for analysis
```{r}
#all models  - no x transformation
MQY_data <- readr::read_csv("csv files/2018.03_AM_HFO_2mo_14d_MQY.csv")

#Check the range of concentration (x) values for the data
unique(MQY_data$raw.x)
```

## Data wrangling/clean-up
```{r}
MQY_data <- readr::read_csv("csv files/2018.03_AM_HFO_2mo_14d_MQY.csv") %>% 
  data.frame() %>% dplyr::mutate(light=as.factor(as.character(light)),
                                 exp_time=as.factor(as.character(exp_time)),
                                 nom.x=as.character(nom.x),
                                 raw.x=as.numeric(as.character(raw.x)),
                                 raw.x=ifelse(raw.x==0, 0.1, raw.x), # deal with 0 concentration values
                                 chamber.ID=as.factor(as.numeric(chamber.ID)),
                                 rep=as.factor(as.numeric(rep)),
                                 tile.ID=as.factor(as.character(tile.ID)),
                                 org.ID=as.factor(as.numeric(org.ID)),
                                 yield=as.numeric(yield),
                                 log.x=log10(raw.x)) # create log values (doesn't really matter if it's log or log10() unless there's a difference in the scaling of the x-data)
str(MQY_data)
head(MQY_data)
tail(MQY_data)
```


## Filter data
```{r}
#filter for exposure time
MQY_14d_data <-MQY_data %>% 
  dplyr::filter(exp_time=="14 days") 

#filter for whether replicates should be included in model fitting
MQY_14d_data <- MQY_14d_data %>% 
  dplyr::filter(use_in_model=="Yes")
  
#filter for light treatment
MQY_14d_PAR_data <- MQY_14d_data %>% 
  dplyr::filter(light=="PAR")
  
MQY_14d_UV_data <- MQY_14d_data %>% 
  dplyr::filter(light=="UVR")

#check that filtering worked
View(MQY_14d_PAR_data)
View(MQY_14d_UV_data)
```


### Save filtered data as an RData object
```{r}
save(MQY_14d_PAR_data, MQY_14d_UV_data, file = "2018.03_AM_HFO_2mo_MQY_14d_data.RData")
```



# PAR/-UV data

## Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2018.03_AM_HFO_2mo_MQY_14d_data.RData")

unique(MQY_14d_PAR_data$raw.x)
par(mfrow=c(2,1))
hist(MQY_14d_PAR_data$raw.x)
hist(MQY_14d_PAR_data$yield)
par(mfrow=c(1,1))
plot(MQY_14d_PAR_data$log.x, MQY_14d_PAR_data$yield) #use this to get an initial visual idea of priors to use (if setting priors manually)
```


## Fit a model-averaged NEC-model (MANEC) using the beta distribution
```{r, eval=FALSE}
load(file = "2018.03_AM_HFO_2mo_MQY_14d_data.RData")

out_MQY_14d_PAR_all <- bayesnec::bnec(yield ~ crf(log.x, model = "decline"),
                                     data = MQY_14d_PAR_data)
save(out_MQY_14d_PAR_all, file = "2018.03_AM_HFO_2mo_MQY_14d_PAR_modfit_all.RData")
beepr::beep("mario")
```

       -> No candidate models could be fitted for the data as the mean CS value of the low concentrations is lower than the mean value for the higher concentrations.



# UV/+UV data

## Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2018.03_AM_HFO_2mo_MQY_14d_data.RData")

unique(MQY_14d_UV_data$raw.x)
par(mfrow=c(2,1))
hist(MQY_14d_UV_data$raw.x)
hist(MQY_14d_UV_data$yield)
par(mfrow=c(1,1))
plot(MQY_14d_UV_data$log.x, MQY_14d_UV_data$yield) #use this to get an initial visual idea of priors to use (if setting priors manually)
```


## Fit a model-averaged NEC-model (MANEC) using the beta distribution
```{r, eval=FALSE}
load(file = "2018.03_AM_HFO_2mo_MQY_14d_data.RData")

out_MQY_14d_UV_all <- bayesnec::bnec(yield ~ crf(log.x, model = "decline"),
                                     data = MQY_14d_UV_data)
save(out_MQY_14d_UV_all, file = "2018.03_AM_HFO_2mo_MQY_14d_UV_modfit_all.RData")
beepr::beep("mario")
```

    -> No candidate models could be fitted for the data as the mean CS value of the low concentrations is lower than the mean value for the higher concentrations.



# Graphical presentation of results
## Concentration-response relationship and raw data
### Complete subset-MANEC plot

Filter raw data to create a start of exposure data object for reference in plotting (if applicable)
```{r}
#filter for exposure time
MQY_0d_data <-MQY_data %>% 
  dplyr::filter(exp_time=="0 days")

#remove samples which should not be included for plotting
MQY_0d_data <- MQY_0d_data %>% 
  dplyr::filter(use_in_plot=="Yes")

#filter for light treatment
MQY_0d_PAR_data <- MQY_0d_data %>% 
  dplyr::filter(light=="PAR")
  
MQY_0d_UV_data <- MQY_0d_data %>% 
  dplyr::filter(light=="UVR")

#replace PAR and UVR with PAR_t0 and UVR_t0
MQY_0d_PAR_data <- MQY_0d_PAR_data %>% 
  dplyr::mutate(light="PAR_t0")
  
MQY_0d_UV_data <- MQY_0d_UV_data %>% 
  dplyr::mutate(light="UVR_t0")

#check that filtering and replacement worked
head(MQY_0d_PAR_data)
head(MQY_0d_UV_data)


save(MQY_0d_PAR_data, MQY_0d_UV_data, file = "2018.03_AM_HFO_2mo_MQY_0d_data.RData")
```

Filter raw data to create holding tank/husbandry data object for reference in plotting (if applicable)
```{r}
#remove samples which should not be included for plotting
MQY_14d_HT_data <- MQY_data %>% 
  dplyr::filter(use_in_plot=="Yes")

#filter for Holding tank samples
MQY_14d_HT_data <- MQY_14d_HT_data %>% 
  dplyr::filter(light=="Holding tank")

#filter for exposure time
MQY_0d_HT_data <-MQY_14d_HT_data %>% 
  dplyr::filter(exp_time=="0 days")
MQY_14d_HT_data <-MQY_14d_HT_data %>% 
  dplyr::filter(exp_time=="14 days")

#check that filtering and replacement worked
head(MQY_0d_HT_data) 
head(MQY_14d_HT_data)

save(MQY_14d_PAR_data, MQY_14d_UV_data, MQY_14d_HT_data, file = "2018.03_AM_HFO_2mo_MQY_14d_data.RData")
save(MQY_0d_PAR_data, MQY_0d_UV_data, file = "2018.03_AM_HFO_2mo_MQY_0d_data.RData")
```

No start of exposure data collected for holding tank/husbandry controls.


```{r}
load("2018.03_AM_HFO_2mo_MQY_14d_data.RData")
load("2018.03_AM_HFO_2mo_MQY_0d_data.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen", "PAR_t0" = "gray75", "UVR_t0" = "gray75", "Holding tank" = "orchid3")) + theme_light() # (add in if plotting t0 or holding tank values)


p.all= p.all+ geom_point(data = MQY_14d_PAR_data, aes(x = raw.x, y = yield, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = MQY_14d_UV_data, aes(x = raw.x, y = yield, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))

#Add in the below if plotting t0 values as comparison
p.all= p.all+ geom_point(data = MQY_0d_PAR_data, aes(x = raw.x, y = yield, colour=factor(light), alpha = 0.3), size = 1.6, position=position_jitter(width = .025, height=0.03), shape = 16)
p.all= p.all+ geom_point(data = MQY_0d_UV_data, aes(x = raw.x, y = yield, colour= factor(light), alpha = 0.3), size = 1.9, position=position_jitter(width = .025, height=0.03), shape = 17)

#Add in the below if plottnig husbandry control/holding tank values as a reference
p.all= p.all+ geom_point(data = MQY_14d_HT_data, aes(x = raw.x, y = yield, colour= factor(light), alpha = 0.3), size = 1.9, position=position_jitter(width = .035, height=0.03), shape = 18)


p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Maximum~quantum~yield),
              subtitle="a)")
p.all= p.all+ scale_y_continuous(limits = c(-0.03, 0.8)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue", "gray75", "gray75")) # (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.09, 500), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_MQY_14dall <- p.all
plot_MQY_14dall
```


