---
title: "2018.03_AM_HFO_2mo_surv_9d"
author: "Mikaela Nordborg"
date: "24/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#For model fitting, evaluation & extraction of results
library(readr)
library(tidyr)
library(dplyr)
require(tidyverse)
library(brms)
library(bayesnec) #devtools::install_github("open-AIMS/bayesnec")
library(beepr)

inv.log10 <- function(x){10^x}

#select usingcmdstanr instead of rtools
require(cmdstanr)
set_cmdstan_path("C:/cmdstan")
options(brms.backend = "cmdstanr")

#For plotting
library(ggplot2)
library(scales)
library(tidybayes)

#For creating layouts & exports
library(ggpubr) #devtools::install_github("kassambara/ggpubr")
```

# Background

Partial survival of 2 month old Acropora millepora corals exposed to the water accommodated fractions (WAF) of heavy fuel oil in the presence or absence of ultraviolet radiation (UV). 

Column headings used:

  date                        = date of assessment/imaging
  exp_time                    = exposure time (days)
  light                       = light treatment corals were exposed under; visible light in the absence (PAR) or presence (UVR) of UV radiation
  nom.x                       = nominal treatment concentration (% WAF)
  raw.x                       = time-averaged, measured treatment concentration (ug TAH/L)
  rep                         = replicate chamber.ID for the treatment combination (1-7)
  chamber.ID                  = exposure chamber used (1-79)
  tile.ID                     = tile number (1-249)
  org.ID                      = identifier for individual corals within a replicate
  area_image_ID               = file identifier for the image file used to obtain live tissue area measurements
  live_area                   = total area of live tissue measured from scaled image files (mm^2)
  area_rel_to_t0              = change in live tissue area at assessment time relative to the area at start of exposure
  surv                        = proportion of live tissue area at start of exposure that remained alive at assessment (0-1)
  comments                    = comments relating to individual data points
  use_in_model                = specifies which data points should be included in statistical analysis
  reason_for_exclusion        = specifies the reason for exclusion form statistical analysis (f applicable)
  use_in_plot                 = specifies whether data should be used in results graphics or not
  reason_for_exclusion_plot   = specifies why data point should not be included in result graphics



# Import and prepare data for analysis
```{r}
#all models  - no x transformation
juv_surv_data <- readr::read_csv("csv files/2018.03_AM_HFO_2mo_14d_surv.csv") 

#Check the range of concentration (x) values for the data
unique(juv_surv_data$raw.x)
```

## Data wrangling/clean-up
```{r}
juv_surv_data <- readr::read_csv("csv files/2018.03_AM_HFO_2mo_14d_surv.csv") %>% 
  data.frame() %>% dplyr::mutate(light=as.factor(as.character(light)),
                                 exp_time=as.factor(as.character(exp_time)),
                                 nom.x=as.character(nom.x),
                                 raw.x=as.numeric(as.character(raw.x)),
                                 raw.x=ifelse(raw.x==0, 0.1, raw.x), # deal with 0 concentration values
                                 rep=as.factor(as.numeric(rep)),
                                 chamber.ID=as.factor(as.numeric(chamber.ID)),
                                 tile.ID=as.factor(as.character(tile.ID)),
                                 org.ID=as.factor(as.numeric(org.ID)),
                                 live_area=as.numeric(as.character(live_area)),
                                 area_rel_to_t0=as.numeric(as.character(area_rel_to_t0)),
                                 surv=as.numeric(surv),
                                 log.x=log10(raw.x), # create log values (doesn't really matter if it's log or log10() unless there's a difference in the scaling of the x-data)
                                 suc=as.integer(surv*20),
                                 tot=as.integer(20)) #to account for the 5% variability in repeat area measurements
str(juv_surv_data)
head(juv_surv_data)
tail(juv_surv_data)
```


## Filter data
```{r}
#filter for exposure time
surv_2mo_9d_data <-juv_surv_data %>% 
  dplyr::filter(exp_time=="9 days") 

#filter for whether replicates should be included in model fitting
surv_2mo_9d_data <- surv_2mo_9d_data %>% 
  dplyr::filter(use_in_model=="Yes")



#filter for light treatment
surv_2mo_9d_PAR_data <- surv_2mo_9d_data %>% 
  dplyr::filter(light=="PAR")
  
surv_2mo_9d_UV_data <- surv_2mo_9d_data %>% 
  dplyr::filter(light=="UVR")

#check that filtering worked
View(surv_2mo_9d_PAR_data)
View(surv_2mo_9d_UV_data)
```


### Save filtered data as an RData object
```{r}
save(surv_2mo_9d_PAR_data, surv_2mo_9d_UV_data, file = "2018.03_AM_HFO_2mo_surv_9d_data.RData")
```



# PAR/-UV data

## Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2018.03_AM_HFO_2mo_surv_9d_data.RData")

unique(surv_2mo_9d_PAR_data$raw.x)
par(mfrow=c(2,1))
hist(surv_2mo_9d_PAR_data$raw.x)
hist(surv_2mo_9d_PAR_data$surv)
par(mfrow=c(1,1))
plot(surv_2mo_9d_PAR_data$log.x, surv_2mo_9d_PAR_data$surv) #use this to get an initial visual idea of priors to use (if setting priors manually)
```


## Fit a model-averaged NEC-model (MANEC) using the betabinomial distribution
```{r, eval=FALSE}
load(file = "2018.03_AM_HFO_2mo_surv_9d_data.RData")


out_surv_2mo_9d_PAR_all <- bayesnec::bnec(suc|trials(tot) ~ crf(log.x, model = "decline"),
                                     data = surv_2mo_9d_PAR_data, family = beta_binomial2)

save(out_surv_2mo_9d_PAR_all, file = "2018.03_AM_HFO_2mo_surv_9d_PAR_modfit_all.RData")
beepr::beep("mario")
```



## Check model fit
Check if any candidate models failed the rHat test
```{r}
load(file = "2018.03_AM_HFO_2mo_surv_9d_PAR_modfit_all.RData")
rhat(out_surv_2mo_9d_PAR_all, rhat_cutoff = 1.03)
```

Drop candidate models that failed the rhat test
```{r}
out_surv_2mo_9d_PAR_mod <- amend(out_surv_2mo_9d_PAR_all, drop = c("ecxexp"))
save(out_surv_2mo_9d_PAR_all, out_surv_2mo_9d_PAR_mod, file = "2018.03_AM_HFO_2mo_surv_9d_PAR_modfit_all.RData")
```

Check model summary
```{r}
out_surv_2mo_9d_PAR_mod$mod_stats
summary(out_surv_2mo_9d_PAR_mod)
```


Check the overall MANEC fit
```{r}
plot(out_surv_2mo_9d_PAR_mod, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
```

Check chain mixing, priors and the fit of the individual candidate models
```{r}
check_chains(out_surv_2mo_9d_PAR_mod, filename = "2018.03_AM_HFO_2mo_surv_9d_PAR_modfit_chains")

check_priors(out_surv_2mo_9d_PAR_mod, filename = "2018.03_AM_HFO_2mo_surv_9d_PAR_modfit_priors")

pdf("2018.03_AM_HFO_2mo_surv_9d_PAR_modfit_fitplots.pdf")
plot(out_surv_2mo_9d_PAR_mod, all_models = TRUE, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
dev.off()
```

  *Any evidence of poor chain mixing or convergence issues?*
      - No
      
 
  *Any indications that the prior distributions were influencing the posterior distributions more than the observed data?*
      - Possibly nec4param (bot) and ecxll5 (bot)

  *Should any of the candidate models be excluded based on the fit relative to the raw data?*
      - No

Drop inappropriate models and models with non-convergence or very poor chain mixing (if required)
```{r}
save(out_surv_2mo_9d_PAR_all, out_surv_2mo_9d_PAR_mod, file = "2018.03_AM_HFO_2mo_surv_9d_PAR_modfit_all.RData")
```


Compare the MANEC containing all OD candidate models to the amended MANEC
```{r}
plot(out_surv_2mo_9d_PAR_all, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
plot(out_surv_2mo_9d_PAR_mod, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```



## Select final MANEC to use

Rename model output for selected MANEC
```{r}
out_surv_2mo_9d_PAR <- out_surv_2mo_9d_PAR_mod
```


Extract the NEC-model subset for use in extraction of NEC and comparisons of posterior distributions
```{r}
out_surv_2mo_9d_PAR_NEC <- pull_out(out_surv_2mo_9d_PAR, model = c("nec"))
```


```{r}
plot(out_surv_2mo_9d_PAR_NEC, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
```


Save the output for the selected models
```{r}
save(out_surv_2mo_9d_PAR, out_surv_2mo_9d_PAR_NEC, file = "2018.03_AM_HFO_2mo_surv_9d_PAR_modfits_final.RData")
load("2018.03_AM_HFO_2mo_surv_9d_PAR_modfits_final.RData")
```



## Extract results

Extract NEC, EC10 and EC50 (with 95% credible intervals) from posterior and backtransform if required
```{r}
NEC_surv_2mo_9d_PAR <- out_surv_2mo_9d_PAR_NEC$w_nec
NEC_surv_2mo_9d_PAR <- 10^NEC_surv_2mo_9d_PAR #if using log10(raw.x)
#NEC_surv_2mo_9d_PAR <- exp(NEC_surv_2mo_9d_PAR) #if using log(raw.x))
NEC_surv_2mo_9d_PAR
```

```{r}
EC10_surv_2mo_9d_PAR <- ecx(out_surv_2mo_9d_PAR, ecx_val = 10, type = "absolute")
EC10_surv_2mo_9d_PAR <- 10^EC10_surv_2mo_9d_PAR #if using log10(raw.x)
#EC10_surv_2mo_9d_PAR <- exp(EC10_surv_2mo_9d_PAR) #if using log(raw.x))
EC10_surv_2mo_9d_PAR
```

```{r}
EC50_surv_2mo_9d_PAR <- ecx(out_surv_2mo_9d_PAR, ecx_val = 50, type = "absolute")
EC50_surv_2mo_9d_PAR <- 10^EC50_surv_2mo_9d_PAR #if using log10(raw.x)
#EC50_surv_2mo_9d_PAR <- exp(EC50_surv_2mo_9d_PAR) #if using log(raw.x))
EC50_surv_2mo_9d_PAR
```


# UV/+UV data

## Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2018.03_AM_HFO_2mo_surv_9d_data.RData")

unique(surv_2mo_9d_UV_data$raw.x)
par(mfrow=c(2,1))
hist(surv_2mo_9d_UV_data$raw.x)
hist(surv_2mo_9d_UV_data$surv)
par(mfrow=c(1,1))
plot(surv_2mo_9d_UV_data$log.x, surv_2mo_9d_UV_data$surv) #use this to get an initial visual idea of priors to use (if setting priors manually)
```


## Fit a model-averaged NEC-model (MANEC) using the betabinomial distribution
```{r, eval=FALSE}
load(file = "2018.03_AM_HFO_2mo_surv_9d_data.RData")

out_surv_2mo_9d_UV_all <- bayesnec::bnec(suc|trials(tot) ~ crf(log.x, model = "decline"),
                                     data = surv_2mo_9d_UV_data, family = beta_binomial2)

save(out_surv_2mo_9d_UV_all, file = "2018.03_AM_HFO_2mo_surv_9d_UV_modfit_all.RData")
beepr::beep("mario")
```



## Check model fit
Check if any candidate models failed the rHat test
```{r}
load(file = "2018.03_AM_HFO_2mo_surv_9d_UV_modfit_all.RData")
rhat(out_surv_2mo_9d_UV_all, rhat_cutoff = 1.03)
```


Check model summary
```{r}
out_surv_2mo_9d_UV_all$mod_stats
summary(out_surv_2mo_9d_UV_all)
```


Check the overall MANEC fit
```{r}
plot(out_surv_2mo_9d_UV_all, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
```

Check chain mixing, priors and the fit of the individual candidate models
```{r}
check_chains(out_surv_2mo_9d_UV_all, filename = "2018.03_AM_HFO_2mo_surv_9d_UV_modfit_chains")

check_priors(out_surv_2mo_9d_UV_all, filename = "2018.03_AM_HFO_2mo_surv_9d_UV_modfit_priors")

pdf("2018.03_AM_HFO_2mo_surv_9d_UV_modfit_fitplots.pdf")
plot(out_surv_2mo_9d_UV_all, all_models = TRUE, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
dev.off()
```

  *Any evidence of poor chain mixing or convergence issues?*
      - model           include/unclear/exclude           Reason for exclusion
      
      - nec3param               exclude                   Some evidence of poor chain mixing
      - nec4param               unclear                   Minor-some evidence of poor chain mixing
      - ecxwb1                  include                   Minor evidence of poor chain mixing
      
  
  *Any indications that the prior distributions were influencing the posterior distributions more than the observed data?*
      - potentially nec4param (bot), ecx4param (bot), ecxwb1 (bot), ecxwb2 (bot), ecxll5 (bot), ecxll4 (bot)

  *Should any of the candidate models be excluded based on the fit relative to the raw data?*
      - ecxexp

Drop inappropriate models and models with non-convergence or very poor chain mixing (if required)
```{r}
out_surv_2mo_9d_UV_mod <- amend(out_surv_2mo_9d_UV_all, drop = c("nec3param", "ecxexp"))

save(out_surv_2mo_9d_UV_all, out_surv_2mo_9d_UV_mod, file = "2018.03_AM_HFO_2mo_surv_9d_UV_modfit_all.RData")
```


Compare the MANEC containing all candidate models to the amended MANEC
```{r}
plot(out_surv_2mo_9d_UV_all, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
plot(out_surv_2mo_9d_UV_mod, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
```



## Select final MANEC to use

Rename model output for selected MANEC
```{r}
out_surv_2mo_9d_UV <- out_surv_2mo_9d_UV_mod
```


Extract the NEC-model subset for use in extraction of NEC and comparisons of posterior distributions
```{r}
out_surv_2mo_9d_UV_NEC <- pull_out(out_surv_2mo_9d_UV, model = c("nec"))
```


```{r}
plot(out_surv_2mo_9d_UV_NEC, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```


Save the output for the selected models
```{r}
save(out_surv_2mo_9d_UV, out_surv_2mo_9d_UV_NEC, file = "2018.03_AM_HFO_2mo_surv_9d_UV_modfits_final.RData")
load("2018.03_AM_HFO_2mo_surv_9d_UV_modfits_final.RData")
```



## Extract results

Extract NEC, EC10 and EC50 (with 95% credible intervals) from posterior and backtransform if required
```{r}
NEC_surv_2mo_9d_UV <- out_surv_2mo_9d_UV_NEC$nec
NEC_surv_2mo_9d_UV <- 10^NEC_surv_2mo_9d_UV #if using log10(raw.x)
#NEC_surv_2mo_9d_UV <- exp(NEC_surv_2mo_9d_UV) #if using log(raw.x))
NEC_surv_2mo_9d_UV
```

```{r}
EC10_surv_2mo_9d_UV <- ecx(out_surv_2mo_9d_UV, ecx_val = 10, type = "absolute")
EC10_surv_2mo_9d_UV <- 10^EC10_surv_2mo_9d_UV #if using log10(raw.x)
#EC10_surv_2mo_9d_UV <- exp(EC10_surv_2mo_9d_UV) #if using log(raw.x))
EC10_surv_2mo_9d_UV
```

```{r}
EC50_surv_2mo_9d_UV <- ecx(out_surv_2mo_9d_UV, ecx_val = 50, type = "absolute")
EC50_surv_2mo_9d_UV <- 10^EC50_surv_2mo_9d_UV #if using log10(raw.x)
#EC50_surv_2mo_9d_UV <- exp(EC50_surv_2mo_9d_UV) #if using log(raw.x))
EC50_surv_2mo_9d_UV
```



# Comparison of light treatments
## Predict response values

Extract complete posteriors for the fitted values using compare_posterior-function
```{r}
load("2018.03_AM_HFO_2mo_surv_9d_PAR_modfits_final.RData")
load("2018.03_AM_HFO_2mo_surv_9d_UV_modfits_final.RData")

pred_surv_2mo_9d <- compare_posterior(x=list("PAR" = out_surv_2mo_9d_PAR, "UVR" = out_surv_2mo_9d_UV), comparison = "fitted", precision = 50)

pred_surv_2mo_9d_PAR <- pred_surv_2mo_9d$posterior_data %>% 
  dplyr::filter(model=="PAR")

pred_surv_2mo_9d_UV <- pred_surv_2mo_9d$posterior_data %>% 
  dplyr::filter(model=="UVR")



pred_surv_2mo_9d_NEC <- compare_posterior(list("PAR" = out_surv_2mo_9d_PAR_NEC, "UVR" = out_surv_2mo_9d_UV_NEC), comparison = "fitted", precision = 50)

pred_surv_2mo_9d_PAR_NEC <- pred_surv_2mo_9d_NEC$posterior_data %>% 
  dplyr::filter(model=="PAR")
pred_surv_2mo_9d_UV_NEC <- pred_surv_2mo_9d_NEC$posterior_data %>% 
 dplyr::filter(model=="UVR")


save(pred_surv_2mo_9d, pred_surv_2mo_9d_PAR, pred_surv_2mo_9d_UV, pred_surv_2mo_9d_PAR_NEC, pred_surv_2mo_9d_UV_NEC, file = "2018.03_AM_HFO_2mo_surv_9d_predvals.RData") # pred_surv_2mo_9d_NEC, pred_surv_2mo_9d_PAR_NEC, pred_surv_2mo_9d_UV_NEC <- add these back in once UV-section is working

load("2018.03_AM_HFO_2mo_surv_9d_predvals.RData")
str(pred_surv_2mo_9d_PAR)
str(pred_surv_2mo_9d_UV)
```


## Determine the highest probability that there is a difference
The highest probability that the two light treatments are different (at any tested x-value) is:
```{r}
load("2018.03_AM_HFO_2mo_surv_9d_predvals.RData")

diff_surv_2mo_9d <- max(pred_surv_2mo_9d$prob_diff$prob)
diff_surv_2mo_9d
```



## EC50

Perform comparison of posterior distributions for partial survival LC50
```{r}
load("2018.03_AM_HFO_2mo_surv_9d_PAR_modfits_final.RData")
load("2018.03_AM_HFO_2mo_surv_9d_UV_modfits_final.RData")

comp_surv_2mo_9dEC50 <- compare_posterior(x=list("PAR" = out_surv_2mo_9d_PAR, "UVR" = out_surv_2mo_9d_UV), comparison = "ecx", ecx_val = 50)
save(comp_surv_2mo_9dEC50, file = "2018.03_AM_HFO_2mo_surv_9d_posterior_comp_EC50.RData")
comp_surv_2mo_9dEC50$prob_diff
```
Table shows the % likelihood that the point estimate calculated (NEC, EC/LC10 or EC/LC50) for model A (in top row) is smaller than the point estimate calculated for model B, C, etc (in left hand column). 

*Is EC50 +UVR lower than the EC50 -UVR?*
    - Not significantly, but there is a trend towards it being lower (with 82.16% probability)




# Graphical presentation of results
## Concentration-response relationship and raw data
### Complete subset-MANEC plot


```{r}
load("2018.03_AM_HFO_2mo_surv_9d_data.RData")
load("2018.03_AM_HFO_2mo_surv_9d_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_surv_2mo_9d_PAR$x, ymin=pred_surv_2mo_9d_PAR$Q2.5, ymax=pred_surv_2mo_9d_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_surv_2mo_9d_UV$x, ymin=pred_surv_2mo_9d_UV$Q2.5, ymax=pred_surv_2mo_9d_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_surv_2mo_9d_PAR$x, y=pred_surv_2mo_9d_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_surv_2mo_9d_UV$x, y=pred_surv_2mo_9d_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = surv_2mo_9d_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = surv_2mo_9d_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Survival~("%")),
              subtitle="a)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.09, 500), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_surv_2mo_9d_all <- p.all
plot_surv_2mo_9d_all
```


### NEC subset-MANEC plot

```{r}
load("2018.03_AM_HFO_2mo_surv_9d_data.RData")
load("2018.03_AM_HFO_2mo_surv_9d_predvals.RData")

p_NEC= ggplot()
p_NEC= p_NEC+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light()


p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_surv_2mo_9d_PAR_NEC$x, ymin=pred_surv_2mo_9d_PAR_NEC$Q2.5, ymax=pred_surv_2mo_9d_PAR_NEC$Q97.5, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
#p_NEC= p_NEC+  scale_fill_manual(values=c("seagreen", "steelblue"))
p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_surv_2mo_9d_UV_NEC$x, ymin=pred_surv_2mo_9d_UV_NEC$Q2.5, ymax=pred_surv_2mo_9d_UV_NEC$Q97.5,fill="steelblue",  alpha=0.3))
#p_NEC= p_NEC+  scale_fill_manual(values="steelblue")


p_NEC= p_NEC+ geom_line(aes(x=10^pred_surv_2mo_9d_PAR_NEC$x, y=pred_surv_2mo_9d_PAR_NEC$Estimate), color = 'grey30', size=0.5)
p_NEC= p_NEC+ geom_line(aes(x=10^pred_surv_2mo_9d_UV_NEC$x, y=pred_surv_2mo_9d_UV_NEC$Estimate), color = 'grey30', size=0.5)


p_NEC= p_NEC+ geom_point(data = surv_2mo_9d_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p_NEC= p_NEC+ geom_point(data = surv_2mo_9d_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))


p_NEC = p_NEC+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})),
              y=expression("9"~d~survival~("%")),
              subtitle="a)")
p_NEC= p_NEC+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p_NEC= p_NEC+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p_NEC= p_NEC+ scale_fill_manual(values = c("seagreen", "steelblue"))
p_NEC= p_NEC+ theme(legend.position="none")
# p_NEC = p_NEC  + theme(legend.position = c(0.9, 0.9))
p_NEC= p_NEC+ scale_x_continuous(limits = c(0.09, 500), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p_NEC= p_NEC+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_surv_2mo_9d_NEC <- p_NEC
plot_surv_2mo_9d_NEC
```


## Comparison of light treatments across concentrations


### Probability of a difference between light treatments plot
Plot the probability of a difference between the UV and PAR light treatments across the treatment concentrations tested
```{r}
load("2018.03_AM_HFO_2mo_surv_9d_predvals.RData")

pred_surv_2mo_9d$prob_diff$inv.x <- 10^pred_surv_2mo_9d$prob_diff$x

p.comp.prob= ggplot(pred_surv_2mo_9d$prob_diff) +
                geom_line(aes(x=inv.x, prob, color="grey"), size=0.8)

p.comp.prob= p.comp.prob + scale_color_manual(values = c("grey")) +
                theme_light() +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80")) +
                theme(legend.position="none") 
    
p.comp.prob= p.comp.prob + scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) +
                scale_x_continuous(limits = c(0.09, 500), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 1000)) +
                labs(x=expression(Treatment~concentration~(μg~TAH~"L"^{-1})),
                      y=expression(Probability~that~UVR~affected~toxicity~("%")),
                      subtitle="a)")

plot_surv_2mo_9d_diff.prob <- p.comp.prob
plot_surv_2mo_9d_diff.prob
```

    If solid line (probability) is higher than 95%/0.95 = UVR significantly increased toxicity at that treatment concentration

### Posterior differences plot
Plot the posterior difference estimate for the UV and PAR light treatments across the treatment concentrations tested
```{r}
load("2018.03_AM_HFO_2mo_surv_9d_predvals.RData")

pred_surv_2mo_9d$diff_data$inv.x <- 10^pred_surv_2mo_9d$diff_data$x

p.comp.diff = ggplot(pred_surv_2mo_9d$diff_data) +
  geom_ribbon(aes(x=inv.x, ymin=diff.Q2.5, ymax=diff.Q97.5, fill = 'grey'), alpha=0.4) +
  geom_line(aes(x=inv.x, diff.Estimate, color="grey"), size=0.8) +
  geom_hline(yintercept = 0, color = "steelblue3", lty = 2, size=0.75)


p.comp.diff= p.comp.diff + scale_fill_manual( values = c("grey", "steelblue3")) +
                scale_color_manual(values = c("grey", "steelblue3")) 
  
p.comp.diff= p.comp.diff + theme_light() + 
                theme(legend.position="none") +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.diff= p.comp.diff + scale_y_continuous(name = "Posterior differences estimate") 
p.comp.diff= p.comp.diff + scale_x_continuous(limits = c(0.09, 500), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100)) +
              labs(x=expression(Treatment~concentration~(μg~TAH~"L"^{-1})),
                  y=expression(Posterior~difference~estimate),
                  subtitle="a)")

plot_surv_2mo_9d_diff.est <- p.comp.diff
plot_surv_2mo_9d_diff.est
```

    If credible intervals (shaded grey area) includes 0 (dotted blue line) there is no significant difference between the two models at that treatment concentration.


## EC50 comparison

Create a custom results plot of the EC50 comparison
```{r}
load("2018.03_AM_HFO_2mo_surv_9d_posterior_comp_EC50.RData")

p.comp.EC50 = ggplot(comp_surv_2mo_9dEC50$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.EC50 = p.comp.EC50 + stat_pointinterval(aes(y = 0.00, x = value, group=model),.width = c(.66, .95), size=0.5)+
  theme_light()

p.comp.EC50 = p.comp.EC50 + scale_fill_manual( values = c("seagreen", "steelblue")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p.comp.EC50 = p.comp.EC50 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50 = p.comp.EC50 + scale_y_continuous(name ="Posterior probability density") 
p.comp.EC50 = p.comp.EC50 + scale_x_continuous(limits = c(-1.02, 2.5), breaks = c(-1, 0, 1, 2), labels = c(0, 1, 10, 100)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.EC50 = p.comp.EC50 + labs(x=expression(), #EC50~(μg~"L"^{-1})
               subtitle="b)")

p.comp.EC50= p.comp.EC50+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 9.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.EC50= p.comp.EC50+ annotate("text", label = "UVR < PAR = 100%", x = 0.55, y = 7.86, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename & show plot
comp.plot_surv_2mo_9d_EC50 <- p.comp.EC50
comp.plot_surv_2mo_9d_EC50
```


Create a custom plot of the EC50 comparisons differences posterior density
```{r}
load("2018.03_AM_HFO_2mo_surv_9d_posterior_comp_EC50.RData")

p.comp.EC50.diff = ggplot(comp_surv_2mo_9dEC50$diff_data, aes(x=diff)) +
  geom_density(aes(x=diff, fill = 'grey'), alpha=0.4) + 
  geom_vline(xintercept = 0, color = "red", lty = 2) + 
  theme_light()

p.comp.EC50.diff = p.comp.EC50.diff + scale_fill_manual( values = c("grey", "grey")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue4", "grey","grey", "grey","grey")) + 
  theme(legend.position="none")
p.comp.EC50.diff = p.comp.EC50.diff + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50.diff = p.comp.EC50.diff + scale_y_continuous(name = "Differences posterior density") 
p.comp.EC50.diff = p.comp.EC50.diff + scale_x_continuous(name = "Standardized effect size") 


#Rename & show plot
comp.plot_surv_2mo_9d_EC50.diff <- p.comp.EC50.diff
comp.plot_surv_2mo_9d_EC50.diff
```




# Create layouts and export (if required)

Create layout to view result plots side-by-side
```{r}
layout_HFO_2mo_surv_9d <- ggarrange(plot_surv_2mo_9d_all, comp.plot_surv_2mo_9d_EC50, plot_surv_2mo_9d_diff.est, plot_surv_2mo_9d_NEC,
          ncol = 3, nrow = 2,
          widths = c(0.5, 0.5))
layout_HFO_2mo_surv_9d
```
