---
title: "2018.03_AM_HFO_post-settlement_results&layouts_v1"
author: "Mikaela Nordborg"
date: "23/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#For model fitting, evaluation & extraction of results
library(readr)
library(tidyr)
library(dplyr)
require(tidyverse)
library(brms)
library(bayesnec) #install from CRAN in the first instance, for intermediate updates use devtools::install_github("open-AIMS/bayesnec")
library(beepr)

inv.log10 <- function(x){10^x}


#For plotting
library(ggplot2)
library(scales)
library(tidybayes)
library(ggdist)

#For creating layouts & exports
library(ggpubr) #devtools::install_github("kassambara/ggpubr")
```

# Layouts

## 1 week old (which go with main text figs)
```{r}
layout.Ch2.SUP.1wo.mainfigs <- ggarrange(plot_surv_1wo_7d_NEC, plot_surv_1wo_7d_diff.est,
          ncol = 2, nrow = 1,
          widths = c(0.5, 0.5))
layout.Ch2.SUP.1wo.mainfigs
```
##### Export
```{r}
pdf("Ch2_SUP_fig_1wo_mainfigs.pdf", width = 6.69, height = 1.95) #height and width in inches
layout.Ch2.SUP.1wo.mainfigs
dev.off()
```



## 2 month old (which go with main text figs)
### 14d post-exposure
```{r}
layout.Ch2.SUP.2mo.mainfigs.diff <- ggarrange(plot_surv_2mo_14dNEC, plot_surv_2mo_14d_diff.est, plot_growth_2mo_14d_NEC, plot_growth_2mo_14d_diff.est,
          ncol = 2, nrow = 2,
          widths = c(0.5, 0.5))
layout.Ch2.SUP.2mo.mainfigs.diff
```
##### Export
```{r}
pdf("Ch2_SUP_fig_2mo_mainfigs_diff.pdf", width = 6.69, height = 3.9) #height and width in inches: 6.69, height = 9.84
layout.Ch2.SUP.2mo.mainfigs.diff
dev.off()
```





### 9d exposure plots
```{r}
layout.Ch2.SUP.2mo.CR.9d.v1 <- ggarrange(plot_surv_2mo_9d_all, plot_surv_2mo_9d_diff.est, plot_growth_2mo_9d_all, plot_growth_2mo_9d_diff.est, plot_CS_9d_all, p.dummy,
          ncol = 2, nrow = 3,
          widths = c(0.5, 0.5))
layout.Ch2.SUP.2mo.CR.9d.v1
```
##### Export
```{r}
pdf("Ch2_SUP_fig_2mo_CR_9d.pdf", width = 6.69, height = 5.85) #height and width in inches: 6.69, height = 9.84
layout.Ch2.SUP.2mo.CR.9d.v1
dev.off()
```


## Dummy plot to fill out spaces

```{r}
p.dummy= ggplot() + theme_light() 
p.dummy + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_blank()) 
p.dummy
```

# Underlying data and plots
## 1 week post-settlement
### End of exposure (7d)
#### Survival
```{r}
load("1wo/2018.01_AM_HFO_1wo_surv_7d_data.RData")
load("1wo/2018.01_AM_HFO_1wo_surv_7d_predvals.RData")

p_NEC= ggplot()
p_NEC= p_NEC+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light()


p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_surv_1wo_7d_PAR_NEC$x, ymin=pred_surv_1wo_7d_PAR_NEC$Q2.5, ymax=pred_surv_1wo_7d_PAR_NEC$Q97.5, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
#p_NEC= p_NEC+  scale_fill_manual(values=c("seagreen", "steelblue"))
p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_surv_1wo_7d_UV_NEC$x, ymin=pred_surv_1wo_7d_UV_NEC$Q2.5, ymax=pred_surv_1wo_7d_UV_NEC$Q97.5,fill="steelblue",  alpha=0.3))
#p_NEC= p_NEC+  scale_fill_manual(values="steelblue")


p_NEC= p_NEC+ geom_line(aes(x=10^pred_surv_1wo_7d_PAR_NEC$x, y=pred_surv_1wo_7d_PAR_NEC$Estimate), color = 'grey30', size=0.5)
p_NEC= p_NEC+ geom_line(aes(x=10^pred_surv_1wo_7d_UV_NEC$x, y=pred_surv_1wo_7d_UV_NEC$Estimate), color = 'grey30', size=0.5)


p_NEC= p_NEC+ geom_point(data = surv_1wo_7d_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p_NEC= p_NEC+ geom_point(data = surv_1wo_7d_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))


p_NEC = p_NEC+ labs(x=expression(),
              y=expression(Survival~("%")),
              subtitle="a)")
p_NEC= p_NEC+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p_NEC= p_NEC+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p_NEC= p_NEC+ scale_fill_manual(values = c("seagreen", "steelblue"))
p_NEC= p_NEC+ theme(legend.position="none")
# p_NEC = p_NEC  + theme(legend.position = c(0.9, 0.9))
p_NEC= p_NEC+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p_NEC= p_NEC+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_surv_1wo_7d_NEC <- p_NEC
plot_surv_1wo_7d_NEC
```

```{r}
load("1wo/2018.01_AM_HFO_1wo_surv_7d_predvals.RData")

pred_surv_1wo_7d$diff_data$inv.x <- 10^pred_surv_1wo_7d$diff_data$x

p.comp.diff = ggplot(pred_surv_1wo_7d$diff_data) +
  geom_ribbon(aes(x=inv.x, ymin=diff.Q2.5, ymax=diff.Q97.5, fill = 'grey'), alpha=0.4) +
  geom_line(aes(x=inv.x, diff.Estimate, color="grey"), size=0.8) +
  geom_hline(yintercept = 0, color = "steelblue3", lty = 2, size=0.75)


p.comp.diff= p.comp.diff + scale_fill_manual( values = c("grey", "steelblue3")) +
                scale_color_manual(values = c("grey", "steelblue3")) 
  
p.comp.diff= p.comp.diff + theme_light() + 
                theme(legend.position="none") +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.diff= p.comp.diff + scale_y_continuous(name = "Posterior differences estimate") 
p.comp.diff= p.comp.diff + scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100)) +
              labs(x=expression(),
                  y=expression(Posterior~difference~estimate),
                  subtitle="b)")

plot_surv_1wo_7d_diff.est <- p.comp.diff
plot_surv_1wo_7d_diff.est
```






## 2 months post-settlement
### Part-way through exposure (9d)
#### Survival
```{r}
load("2mo/2018.03_AM_HFO_2mo_surv_9d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_surv_9d_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_surv_2mo_9d_PAR$x, ymin=pred_surv_2mo_9d_PAR$Q2.5, ymax=pred_surv_2mo_9d_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_surv_2mo_9d_UV$x, ymin=pred_surv_2mo_9d_UV$Q2.5, ymax=pred_surv_2mo_9d_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_surv_2mo_9d_PAR$x, y=pred_surv_2mo_9d_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_surv_2mo_9d_UV$x, y=pred_surv_2mo_9d_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = surv_2mo_9d_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = surv_2mo_9d_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Survival~("%")),
              subtitle="a)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_surv_2mo_9d_all <- p.all
plot_surv_2mo_9d_all
```

```{r}
load("2mo/2018.03_AM_HFO_2mo_surv_9d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_surv_9d_predvals.RData")

p_NEC= ggplot()
p_NEC= p_NEC+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light()


p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_surv_2mo_9d_PAR_NEC$x, ymin=pred_surv_2mo_9d_PAR_NEC$Q2.5, ymax=pred_surv_2mo_9d_PAR_NEC$Q97.5, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
#p_NEC= p_NEC+  scale_fill_manual(values=c("seagreen", "steelblue"))
p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_surv_2mo_9d_UV_NEC$x, ymin=pred_surv_2mo_9d_UV_NEC$Q2.5, ymax=pred_surv_2mo_9d_UV_NEC$Q97.5,fill="steelblue",  alpha=0.3))
#p_NEC= p_NEC+  scale_fill_manual(values="steelblue")


p_NEC= p_NEC+ geom_line(aes(x=10^pred_surv_2mo_9d_PAR_NEC$x, y=pred_surv_2mo_9d_PAR_NEC$Estimate), color = 'grey30', size=0.5)
p_NEC= p_NEC+ geom_line(aes(x=10^pred_surv_2mo_9d_UV_NEC$x, y=pred_surv_2mo_9d_UV_NEC$Estimate), color = 'grey30', size=0.5)


p_NEC= p_NEC+ geom_point(data = surv_2mo_9d_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p_NEC= p_NEC+ geom_point(data = surv_2mo_9d_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))


p_NEC = p_NEC+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Survival~("%")),
              subtitle="a) 9 day exposure")
p_NEC= p_NEC+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p_NEC= p_NEC+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p_NEC= p_NEC+ scale_fill_manual(values = c("seagreen", "steelblue"))
p_NEC= p_NEC+ theme(legend.position="none")
# p_NEC = p_NEC  + theme(legend.position = c(0.9, 0.9))
p_NEC= p_NEC+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p_NEC= p_NEC+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_surv_2mo_9d_NEC <- p_NEC
plot_surv_2mo_9d_NEC
```

```{r}
load("2mo/2018.03_AM_HFO_2mo_surv_9d_predvals.RData")

pred_surv_2mo_9d$diff_data$inv.x <- 10^pred_surv_2mo_9d$diff_data$x

p.comp.diff = ggplot(pred_surv_2mo_9d$diff_data) +
  geom_ribbon(aes(x=inv.x, ymin=diff.Q2.5, ymax=diff.Q97.5, fill = 'grey'), alpha=0.4) +
  geom_line(aes(x=inv.x, diff.Estimate, color="grey"), size=0.8) +
  geom_hline(yintercept = 0, color = "steelblue3", lty = 2, size=0.75)


p.comp.diff= p.comp.diff + scale_fill_manual( values = c("grey", "steelblue3")) +
                scale_color_manual(values = c("grey", "steelblue3")) 
  
p.comp.diff= p.comp.diff + theme_light() + 
                theme(legend.position="none") +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.diff= p.comp.diff + scale_y_continuous(name = "Posterior differences estimate") 
p.comp.diff= p.comp.diff + scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100)) +
              labs(x=expression(),
                  y=expression(),
                  subtitle="b)")

plot_surv_2mo_9d_diff.est <- p.comp.diff
plot_surv_2mo_9d_diff.est
```

#### Relative growth
```{r}
load("2mo/2018.03_AM_HFO_2mo_growth_9d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_growth_9d_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_growth_2mo_9d_PAR$x, ymin=pred_growth_2mo_9d_PAR$Q2.5, ymax=pred_growth_2mo_9d_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_growth_2mo_9d_UV$x, ymin=pred_growth_2mo_9d_UV$Q2.5, ymax=pred_growth_2mo_9d_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_growth_2mo_9d_PAR$x, y=pred_growth_2mo_9d_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_growth_2mo_9d_UV$x, y=pred_growth_2mo_9d_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = growth_2mo_9d_PAR_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = growth_2mo_9d_UV_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Relative~growth~("%")),
              subtitle="c)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.37), breaks = c(0, 0.25, 0.5, 0.75, 1., 1.25), labels = c(0, 25, 50, 75, 100, 125))
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_growth_2mo_9d_all <- p.all
plot_growth_2mo_9d_all
```

```{r}
load("2mo/2018.03_AM_HFO_2mo_growth_9d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_growth_9d_predvals.RData")

p_NEC= ggplot()
p_NEC= p_NEC+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light()


p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_growth_2mo_9d_PAR_NEC$x, ymin=pred_growth_2mo_9d_PAR_NEC$Q2.5, ymax=pred_growth_2mo_9d_PAR_NEC$Q97.5, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
#p_NEC= p_NEC+  scale_fill_manual(values=c("seagreen", "steelblue"))
p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_growth_2mo_9d_UV_NEC$x, ymin=pred_growth_2mo_9d_UV_NEC$Q2.5, ymax=pred_growth_2mo_9d_UV_NEC$Q97.5,fill="steelblue",  alpha=0.3))
#p_NEC= p_NEC+  scale_fill_manual(values="steelblue")


p_NEC= p_NEC+ geom_line(aes(x=10^pred_growth_2mo_9d_PAR_NEC$x, y=pred_growth_2mo_9d_PAR_NEC$Estimate), color = 'grey30', size=0.5)
p_NEC= p_NEC+ geom_line(aes(x=10^pred_growth_2mo_9d_UV_NEC$x, y=pred_growth_2mo_9d_UV_NEC$Estimate), color = 'grey30', size=0.5)


p_NEC= p_NEC+ geom_point(data = growth_2mo_9d_PAR_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p_NEC= p_NEC+ geom_point(data = growth_2mo_9d_UV_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))


p_NEC = p_NEC+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})),
              y=expression(Relative~growth~("%")),
              subtitle="c)")
p_NEC= p_NEC+ scale_y_continuous( limits = c(-0.03, 1.36), breaks = c(0, 0.25, 0.5, 0.75, 1.0, 1.25), labels = c(0, 25, 50, 75, 100, 125)) 
p_NEC= p_NEC+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p_NEC= p_NEC+ scale_fill_manual(values = c("seagreen", "steelblue"))
p_NEC= p_NEC+ theme(legend.position="none")
# p_NEC = p_NEC  + theme(legend.position = c(0.9, 0.9))
p_NEC= p_NEC+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p_NEC= p_NEC+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_growth_2mo_9d_NEC <- p_NEC
plot_growth_2mo_9d_NEC
```

```{r}
load("2mo/2018.03_AM_HFO_2mo_growth_9d_predvals.RData")

pred_growth_2mo_9d$diff_data$inv.x <- 10^pred_growth_2mo_9d$diff_data$x

p.comp.diff = ggplot(pred_growth_2mo_9d$diff_data) +
  geom_ribbon(aes(x=inv.x, ymin=diff.Q2.5, ymax=diff.Q97.5, fill = 'grey'), alpha=0.4) +
  geom_line(aes(x=inv.x, diff.Estimate, color="grey"), size=0.8) +
  geom_hline(yintercept = 0, color = "steelblue3", lty = 2, size=0.75)


p.comp.diff= p.comp.diff + scale_fill_manual( values = c("grey", "steelblue3")) +
                scale_color_manual(values = c("grey", "steelblue3")) 
  
p.comp.diff= p.comp.diff + theme_light() + 
                theme(legend.position="none") +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.diff= p.comp.diff + scale_y_continuous(name = "Posterior differences estimate") 
p.comp.diff= p.comp.diff + scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100)) +
              labs(x=expression(Concentration~(μg~TAH~"L"^{-1})),
                  y=expression(Posterior~difference~estimate),
                  subtitle="d)")

plot_growth_2mo_9d_diff.est <- p.comp.diff
plot_growth_2mo_9d_diff.est
```


#### Coral colour score
```{r}
load("2mo/2018.03_AM_HFO_2mo_CS_9d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_CS_0d_data.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen", "PAR_t0" = "gray75", "UVR_t0" = "gray75", "Holding tank" = "orchid3")) + theme_light() # (add in if plotting t0 values)


#Add in the below if plotting t0 values as comparison
p.all= p.all+ geom_point(data = CS_0d_PAR_data, aes(x = raw.x, y = CS, colour=factor(light), alpha = 0.3), size = 1.6, position=position_jitter(width = .035, height=0.03), shape = 16)
p.all= p.all+ geom_point(data = CS_0d_UV_data, aes(x = raw.x, y = CS, colour= factor(light), alpha = 0.3), size = 1.9, position=position_jitter(width = .035, height=0.03), shape = 17)

p.all= p.all+ geom_point(data = CS_9d_PAR_data, aes(x = raw.x, y = CS, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .035, height=0.03))
p.all= p.all+ geom_point(data = CS_9d_UV_data, aes(x = raw.x, y = CS, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .035, height=0.03))



#Add in the below if plotting husbandry control/holding tank values as a reference
p.all= p.all+ geom_point(data = CS_0d_HT_data, aes(x = raw.x, y = CS, colour=factor(light), alpha = 0.3), size = 1.6, position=position_jitter(width = .035, height=0.03), shape = 18)


p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Coral~colour~score),
              subtitle="e)")
p.all= p.all+ scale_y_continuous(limits = c(-0.03, 7)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue", "gray75", "gray75")) # (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_CS_9d_all <- p.all
plot_CS_9d_all
```

NEC subset MANEC plot - NA

Posterior differences plot - NA



### End of exposure (14d)
#### Survival
```{r}
load("2mo/2018.03_AM_HFO_2mo_surv_14d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_surv_14d_predvals.RData")

p_NEC= ggplot()
p_NEC= p_NEC+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light()


p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_surv_2mo_14d_PAR_NEC$x, ymin=pred_surv_2mo_14d_PAR_NEC$Q2.5, ymax=pred_surv_2mo_14d_PAR_NEC$Q97.5, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
#p_NEC= p_NEC+  scale_fill_manual(values=c("seagreen", "steelblue"))
p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_surv_2mo_14d_UV_NEC$x, ymin=pred_surv_2mo_14d_UV_NEC$Q2.5, ymax=pred_surv_2mo_14d_UV_NEC$Q97.5,fill="steelblue",  alpha=0.3))
#p_NEC= p_NEC+  scale_fill_manual(values="steelblue")


p_NEC= p_NEC+ geom_line(aes(x=10^pred_surv_2mo_14d_PAR_NEC$x, y=pred_surv_2mo_14d_PAR_NEC$Estimate), color = 'grey30', size=0.5)
p_NEC= p_NEC+ geom_line(aes(x=10^pred_surv_2mo_14d_UV_NEC$x, y=pred_surv_2mo_14d_UV_NEC$Estimate), color = 'grey30', size=0.5)


p_NEC= p_NEC+ geom_point(data = surv_2mo_14d_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p_NEC= p_NEC+ geom_point(data = surv_2mo_14d_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))


p_NEC = p_NEC+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Survival~("%")),
              subtitle="a)")
p_NEC= p_NEC+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p_NEC= p_NEC+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p_NEC= p_NEC+ scale_fill_manual(values = c("seagreen", "steelblue"))
p_NEC= p_NEC+ theme(legend.position="none")
# p_NEC = p_NEC  + theme(legend.position = c(0.9, 0.9))
p_NEC= p_NEC+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p_NEC= p_NEC+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_surv_2mo_14dNEC <- p_NEC
plot_surv_2mo_14dNEC
```

```{r}
load("2mo/2018.03_AM_HFO_2mo_surv_14d_predvals.RData")

pred_surv_2mo_14d$diff_data$inv.x <- 10^pred_surv_2mo_14d$diff_data$x

p.comp.diff = ggplot(pred_surv_2mo_14d$diff_data) +
  geom_ribbon(aes(x=inv.x, ymin=diff.Q2.5, ymax=diff.Q97.5, fill = 'grey'), alpha=0.4) +
  geom_line(aes(x=inv.x, diff.Estimate, color="grey"), size=0.8) +
  geom_hline(yintercept = 0, color = "steelblue3", lty = 2, size=0.75)


p.comp.diff= p.comp.diff + scale_fill_manual( values = c("grey", "steelblue3")) +
                scale_color_manual(values = c("grey", "steelblue3")) 
  
p.comp.diff= p.comp.diff + theme_light() + 
                theme(legend.position="none") +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.diff= p.comp.diff + scale_y_continuous(name = "Posterior differences estimate") 
p.comp.diff= p.comp.diff + scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100)) +
              labs(x=expression(),
                  y=expression(),
                  subtitle="b)")

plot_surv_2mo_14d_diff.est <- p.comp.diff
plot_surv_2mo_14d_diff.est
```

#### Relative growth
```{r}
load("2mo/2018.03_AM_HFO_2mo_growth_14d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_growth_14d_predvals.RData")

p_NEC= ggplot()
p_NEC= p_NEC+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light()


p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_growth_2mo_14d_PAR_NEC$x, ymin=pred_growth_2mo_14d_PAR_NEC$Q2.5, ymax=pred_growth_2mo_14d_PAR_NEC$Q97.5, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
#p_NEC= p_NEC+  scale_fill_manual(values=c("seagreen", "steelblue"))
p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_growth_2mo_14d_UV_NEC$x, ymin=pred_growth_2mo_14d_UV_NEC$Q2.5, ymax=pred_growth_2mo_14d_UV_NEC$Q97.5,fill="steelblue",  alpha=0.3))
#p_NEC= p_NEC+  scale_fill_manual(values="steelblue")


p_NEC= p_NEC+ geom_line(aes(x=10^pred_growth_2mo_14d_PAR_NEC$x, y=pred_growth_2mo_14d_PAR_NEC$Estimate), color = 'grey30', size=0.5)
p_NEC= p_NEC+ geom_line(aes(x=10^pred_growth_2mo_14d_UV_NEC$x, y=pred_growth_2mo_14d_UV_NEC$Estimate), color = 'grey30', size=0.5)


p_NEC= p_NEC+ geom_point(data = growth_2mo_14d_PAR_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p_NEC= p_NEC+ geom_point(data = growth_2mo_14d_UV_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))


p_NEC = p_NEC+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})),
              y=expression(Relative~growth~("%")),
              subtitle="c)")
p_NEC= p_NEC+ scale_y_continuous( limits = c(-0.03, 1.36), breaks = c(0, 0.25, 0.5, 0.75, 1.0, 1.25), labels = c(0, 25, 50, 75, 100, 125)) 
p_NEC= p_NEC+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p_NEC= p_NEC+ scale_fill_manual(values = c("seagreen", "steelblue"))
p_NEC= p_NEC+ theme(legend.position="none")
# p_NEC = p_NEC  + theme(legend.position = c(0.9, 0.9))
p_NEC= p_NEC+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p_NEC= p_NEC+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_growth_2mo_14d_NEC <- p_NEC
plot_growth_2mo_14d_NEC
```

```{r}
load("2mo/2018.03_AM_HFO_2mo_growth_14d_predvals.RData")

pred_growth_2mo_14d$diff_data$inv.x <- 10^pred_growth_2mo_14d$diff_data$x

p.comp.diff = ggplot(pred_growth_2mo_14d$diff_data) +
  geom_ribbon(aes(x=inv.x, ymin=diff.Q2.5, ymax=diff.Q97.5, fill = 'grey'), alpha=0.4) +
  geom_line(aes(x=inv.x, diff.Estimate, color="grey"), size=0.8) +
  geom_hline(yintercept = 0, color = "steelblue3", lty = 2, size=0.75)


p.comp.diff= p.comp.diff + scale_fill_manual( values = c("grey", "steelblue3")) +
                scale_color_manual(values = c("grey", "steelblue3")) 
  
p.comp.diff= p.comp.diff + theme_light() + 
                theme(legend.position="none") +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.diff= p.comp.diff + scale_y_continuous(name = "Posterior differences estimate") 
p.comp.diff= p.comp.diff + scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100)) +
              labs(x=expression(Concentration~(μg~TAH~"L"^{-1})),
                  y=expression(Posterior~difference~estimate),
                  subtitle="d)")

plot_growth_2mo_14d_diff.est <- p.comp.diff
plot_growth_2mo_14d_diff.est
```



#### Coral colour score

NEC subset MANEC plot - NA

Posterior differences plot - NA



#### Maximum quantum yield

NEC subset MANEC plot - NA

Posterior differences plot - NA


