---
title: "2018.03_AM_HFO_post-settlement_results&layouts_v1"
author: "Mikaela Nordborg"
date: "23/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#For model fitting, evaluation & extraction of results
library(readr)
library(tidyr)
library(dplyr)
require(tidyverse)
library(brms)
library(bayesnec) #install from CRAN in the first instance, for intermediate updates use devtools::install_github("open-AIMS/bayesnec")
library(beepr)

inv.log10 <- function(x){10^x}


#For plotting
library(ggplot2)
library(scales)
library(tidybayes)
library(ggdist)

#For creating layouts & exports
library(ggpubr) #devtools::install_github("kassambara/ggpubr")
```

# Main text

## Layouts
### Full MANEC fit layouts
#### 1wo end of exposure
##### version 2
```{r}
layout.Ch2.main.1wo.CR.v2 <- ggarrange(plot_surv_1wo_7d_all, plot_lat_surv_1wo_8dpe_all, plot_lat_growth_1wo_8dpe_all, plot_lat_symb_1wo_8dpe_all,
          ncol = 1, nrow = 4,
          widths = c(0.5, 0.5))
layout.Ch2.main.1wo.CR.v2
```
###### Export
```{r}
pdf("Ch2_Main_fig_1wo_CR.pdf", width = 3.345, height = 9.6) #height and width in inches
layout.Ch2.main.1wo.CR.v2
dev.off()
```

##### version 3
```{r}
layout.Ch2.main.1wo.CR.v3 <- ggarrange(plot_surv_1wo_7d_all, plot_lat_surv_1wo_6wpe_all, plot_lat_growth_1wo_8dpe_all, plot_lat_growth_1wo_6wpe_all, plot_lat_symb_1wo_8dpe_all, plot_lat_symb_1wo_6wpe_all,
          ncol = 2, nrow = 3,
          widths = c(0.5, 0.5))
layout.Ch2.main.1wo.CR.v3
```
###### Export
```{r}
pdf("Ch2_Main_fig_1wo_CR.pdf", width = 6.69, height = 7.8) #height and width in inches
layout.Ch2.main.1wo.CR.v3
dev.off()
```


#### 14 d exposure

##### Figure 2
```{r}
layout.Ch2.main.2mo.CR.9_14d.v2 <- ggarrange(plot_surv_2mo_14d_all, plot_lat_surv_2mo_6wpe_all, plot_growth_2mo_14d_all, plot_lat_growth_2mo_6wpe_all,
          ncol = 2, nrow = 2,
          widths = c(0.5, 0.5))
layout.Ch2.main.2mo.CR.9_14d.v2
```
##### Export
```{r}
pdf("Ch2_Main_fig_2mo_CR_Suv&Grow.pdf", width = 6.69, height = 5.2) #height and width in inches: 6.69, height = 9.84
layout.Ch2.main.2mo.CR.9_14d.v2
dev.off()
```


##### Figure 3
```{r}
layout.Ch2.main.2mo.CR.9_14d.v3 <- ggarrange(plot_CS_14d_all, plot_MQY_14dall,
          ncol = 2, nrow = 1,
          widths = c(0.5, 0.5))
layout.Ch2.main.2mo.CR.9_14d.v3
```
##### Export
```{r}
pdf("Ch2_Main_fig_2mo_CR_CS&MQY.pdf", width = 6.69, height = 2.6) #height and width in inches: 6.69, height = 9.84
layout.Ch2.main.2mo.CR.9_14d.v3
dev.off()
```



## Dummy plot to fill out spaces

```{r}
p.dummy= ggplot() + theme_light() 
p.dummy + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_blank()) 
p.dummy
```



# Underlying data and graphics
## 1 week post-settlement

### End of exposure (7d)
#### Survival
```{r}
load("1wo/2018.01_AM_HFO_1wo_surv_7d_data.RData")
load("1wo/2018.01_AM_HFO_1wo_surv_7d_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_surv_1wo_7d_PAR$x, ymin=pred_surv_1wo_7d_PAR$Q2.5, ymax=pred_surv_1wo_7d_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_surv_1wo_7d_UV$x, ymin=pred_surv_1wo_7d_UV$Q2.5, ymax=pred_surv_1wo_7d_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_surv_1wo_7d_PAR$x, y=pred_surv_1wo_7d_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_surv_1wo_7d_UV$x, y=pred_surv_1wo_7d_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = surv_1wo_7d_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = surv_1wo_7d_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Survival~("%")),
              subtitle="a) End of exposure")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_surv_1wo_7d_all <- p.all
plot_surv_1wo_7d_all
```


### Post-exposure
#### Latent survival
##### 8 days post-exposure
```{r}
load("1wo/2018.01_AM_HFO_1wo_lat_surv_8dpe_data.RData")
load("1wo/2018.01_AM_HFO_1wo_lat_surv_8dpe_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_surv_1wo_8dpe_PAR$x, ymin=pred_lat_surv_1wo_8dpe_PAR$Q2.5, ymax=pred_lat_surv_1wo_8dpe_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_surv_1wo_8dpe_UV$x, ymin=pred_lat_surv_1wo_8dpe_UV$Q2.5, ymax=pred_lat_surv_1wo_8dpe_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_lat_surv_1wo_8dpe_PAR$x, y=pred_lat_surv_1wo_8dpe_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_lat_surv_1wo_8dpe_UV$x, y=pred_lat_surv_1wo_8dpe_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = surv_1wo_8dpe_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = surv_1wo_8dpe_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Latent~survival~("%")), #Latent~survival~("%")
              subtitle="b) 8 days post-exposure")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_surv_1wo_8dpe_all <- p.all
plot_lat_surv_1wo_8dpe_all
```

##### 6 weeks post-exposure
```{r}
load("1wo/2018.01_AM_HFO_1wo_lat_surv_6wpe_data.RData")
load("1wo/2018.01_AM_HFO_1wo_lat_surv_6wpe_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_surv_1wo_6wpe_PAR$x, ymin=pred_lat_surv_1wo_6wpe_PAR$Q2.5, ymax=pred_lat_surv_1wo_6wpe_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_surv_1wo_6wpe_UV$x, ymin=pred_lat_surv_1wo_6wpe_UV$Q2.5, ymax=pred_lat_surv_1wo_6wpe_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_lat_surv_1wo_6wpe_PAR$x, y=pred_lat_surv_1wo_6wpe_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_lat_surv_1wo_6wpe_UV$x, y=pred_lat_surv_1wo_6wpe_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = surv_1wo_6wpe_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = surv_1wo_6wpe_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(), #Latent~survival~("%")
              subtitle="b) 6 weeks post-exposure")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_surv_1wo_6wpe_all <- p.all
plot_lat_surv_1wo_6wpe_all
```

#### Latent relative growth
##### 8 days post-exposure
```{r}
load("1wo/2018.01_AM_HFO_1wo_lat_growth_8dpe_data.RData")
load("1wo/2018.01_AM_HFO_1wo_lat_growth_8dpe_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_growth_1wo_8dpe_PAR$x, ymin=pred_lat_growth_1wo_8dpe_PAR$Q2.5, ymax=pred_lat_growth_1wo_8dpe_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_growth_1wo_8dpe_UV$x, ymin=pred_lat_growth_1wo_8dpe_UV$Q2.5, ymax=pred_lat_growth_1wo_8dpe_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_lat_growth_1wo_8dpe_PAR$x, y=pred_lat_growth_1wo_8dpe_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_lat_growth_1wo_8dpe_UV$x, y=pred_lat_growth_1wo_8dpe_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = growth_1wo_8dpe_PAR_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = growth_1wo_8dpe_UV_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Latent~relative~growth~("%")),
              subtitle="c) 8 days post-exposure")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_growth_1wo_8dpe_all <- p.all
plot_lat_growth_1wo_8dpe_all
```

##### 6 weeks post-exposure
```{r}
load("1wo/2018.01_AM_HFO_1wo_lat_growth_6wpe_data.RData")
load("1wo/2018.01_AM_HFO_1wo_lat_growth_6wpe_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_growth_1wo_6wpe_PAR$x, ymin=pred_lat_growth_1wo_6wpe_PAR$Q2.5, ymax=pred_lat_growth_1wo_6wpe_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
#p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_growth_1wo_6wpe_UV$x, ymin=pred_lat_growth_1wo_6wpe_UV$Q2.5, ymax=pred_lat_growth_1wo_6wpe_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_lat_growth_1wo_6wpe_PAR$x, y=pred_lat_growth_1wo_6wpe_PAR$Estimate), color = 'grey30', size=0.5)
#p.all= p.all+ geom_line(aes(x=10^pred_lat_growth_1wo_6wpe_UV$x, y=pred_lat_growth_1wo_6wpe_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = growth_1wo_6wpe_PAR_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = growth_1wo_6wpe_UV_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(), #Latent~relative~growth~("%")
              subtitle="d)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 16.05), breaks = c(0, 5, 10, 15.0), labels = c(0, 500, 1000, 1500)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_growth_1wo_6wpe_all <- p.all
plot_lat_growth_1wo_6wpe_all
```


#### Symbiont uptake/presence
##### 8 days post-exposure
```{r}
load("1wo/2018.01_AM_HFO_1wo_lat_symb_8dpe_data.RData")
load("1wo/2018.01_AM_HFO_1wo_lat_symb_8dpe_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_symb_1wo_8dpe_PAR$x, ymin=pred_lat_symb_1wo_8dpe_PAR$Q2.5, ymax=pred_lat_symb_1wo_8dpe_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_symb_1wo_8dpe_UV$x, ymin=pred_lat_symb_1wo_8dpe_UV$Q2.5, ymax=pred_lat_symb_1wo_8dpe_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_lat_symb_1wo_8dpe_PAR$x, y=pred_lat_symb_1wo_8dpe_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_lat_symb_1wo_8dpe_UV$x, y=pred_lat_symb_1wo_8dpe_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ stat_dots(data = symb_1wo_8dpe_PAR_data, aes(x = raw.x, y = symbionts, colour=factor(light), shape = factor(light), alpha = 0.3, side = ifelse(symbionts == 0, "top", "bottom")), scale = 1.0, position=position_jitter(width = .07, height=0)) 
p.all= p.all+ stat_dots(data = symb_1wo_8dpe_UV_data, aes(x = raw.x, y = symbionts, colour=factor(light), shape = factor(light), alpha = 0.3, side = ifelse(symbionts == 0, "top", "bottom")), scale = 1.0, position=position_jitter(width = .07, height=0)) 



p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Algal~symbionts~observed),
              subtitle="e) 8 days post-exposure")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 1.0), labels = c("No", "Yes")) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_symb_1wo_8dpe_all <- p.all
plot_lat_symb_1wo_8dpe_all
```


##### 6 weeks post-exposure
```{r}
load("1wo/2018.01_AM_HFO_1wo_lat_symb_6wpe_data.RData")
#load("2018.01_AM_HFO_1wo_lat_symb_6wpe_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


#p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_symb_1wo_6wpe_PAR$x, ymin=pred_lat_symb_1wo_6wpe_PAR$Q2.5, ymax=pred_lat_symb_1wo_6wpe_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
#p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_symb_1wo_6wpe_UV$x, ymin=pred_lat_symb_1wo_6wpe_UV$Q2.5, ymax=pred_lat_symb_1wo_6wpe_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


#p.all= p.all+ geom_line(aes(x=10^pred_lat_symb_1wo_6wpe_PAR$x, y=pred_lat_symb_1wo_6wpe_PAR$Estimate), color = 'grey30', size=0.5)
#p.all= p.all+ geom_line(aes(x=10^pred_lat_symb_1wo_6wpe_UV$x, y=pred_lat_symb_1wo_6wpe_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ stat_dots(data = symb_1wo_6wpe_PAR_data, aes(x = raw.x, y = symbionts, colour=factor(light), shape = factor(light), alpha = 0.3, side = ifelse(symbionts == 0, "top", "bottom")), scale = 1.0, position=position_jitter(width = .07, height=0))
p.all= p.all+ stat_dots(data = symb_1wo_6wpe_UV_data, aes(x = raw.x, y = symbionts, colour=factor(light), shape = factor(light), alpha = 0.3, side = ifelse(symbionts == 0, "top", "bottom")), scale = 1.0, position=position_jitter(width = .07, height=0))

#p.all= p.all+ geom_point(data = symb_1wo_6wpe_PAR_data, aes(x = raw.x, y = symbionts, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
#p.all= p.all+ geom_point(data = symb_1wo_6wpe_UV_data, aes(x = raw.x, y = symbionts, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))

#p.all= p.all+ geom_hline(yintercept = 0.5, color = "grey30", lty = 2, size=0.5)


p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(),
              subtitle="f)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 1.0), labels = c("No", "Yes")) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_symb_1wo_6wpe_all <- p.all
plot_lat_symb_1wo_6wpe_all
```


## 2 months post-settlement
### End of exposure (14d)
#### Survival
```{r}
load("2mo/2018.03_AM_HFO_2mo_surv_14d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_surv_14d_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_surv_2mo_14d_PAR$x, ymin=pred_surv_2mo_14d_PAR$Q2.5, ymax=pred_surv_2mo_14d_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_surv_2mo_14d_UV$x, ymin=pred_surv_2mo_14d_UV$Q2.5, ymax=pred_surv_2mo_14d_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_surv_2mo_14d_PAR$x, y=pred_surv_2mo_14d_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_surv_2mo_14d_UV$x, y=pred_surv_2mo_14d_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = surv_2mo_14d_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = surv_2mo_14d_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Survival~("%")), #Survival~("%")
              subtitle="a) End of exposure")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_surv_2mo_14d_all <- p.all
plot_surv_2mo_14d_all
```
##### 6 weeks post-exposure
```{r}
load("2mo/2018.03_AM_HFO_2mo_lat_surv_6wpe_data.RData")
load("2mo/2018.03_AM_HFO_2mo_lat_surv_6wpe_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_surv_2mo_6wpe_PAR$x, ymin=pred_lat_surv_2mo_6wpe_PAR$Q2.5, ymax=pred_lat_surv_2mo_6wpe_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_surv_2mo_6wpe_UV$x, ymin=pred_lat_surv_2mo_6wpe_UV$Q2.5, ymax=pred_lat_surv_2mo_6wpe_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_lat_surv_2mo_6wpe_PAR$x, y=pred_lat_surv_2mo_6wpe_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_lat_surv_2mo_6wpe_UV$x, y=pred_lat_surv_2mo_6wpe_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = surv_2mo_6wpe_PAR_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = surv_2mo_6wpe_UV_data, aes(x = raw.x, y = surv, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(), #Survival~("%")
              subtitle="b) 6 weeks post-exposure")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_surv_2mo_6wpe_all <- p.all
plot_lat_surv_2mo_6wpe_all
```


#### Relative growth
```{r}
load("2mo/2018.03_AM_HFO_2mo_growth_14d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_growth_14d_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_growth_2mo_14d_PAR$x, ymin=pred_growth_2mo_14d_PAR$Q2.5, ymax=pred_growth_2mo_14d_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_growth_2mo_14d_UV$x, ymin=pred_growth_2mo_14d_UV$Q2.5, ymax=pred_growth_2mo_14d_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_growth_2mo_14d_PAR$x, y=pred_growth_2mo_14d_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_growth_2mo_14d_UV$x, y=pred_growth_2mo_14d_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = growth_2mo_14d_PAR_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = growth_2mo_14d_UV_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Relative~growth~("%")), #Relative~growth~("%")
              subtitle="c)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.55), breaks = c(0, 0.5, 1, 1.5), labels = c(0, 50, 100, 150)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_growth_2mo_14d_all <- p.all
plot_growth_2mo_14d_all
```

##### 6 weeks post-exposure
```{r}
load("2mo/2018.03_AM_HFO_2mo_lat_growth_6wpe_data.RData")
load("2mo/2018.03_AM_HFO_2mo_lat_growth_6wpe_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_growth_2mo_6wpe_PAR$x, ymin=pred_lat_growth_2mo_6wpe_PAR$Q2.5, ymax=pred_lat_growth_2mo_6wpe_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_growth_2mo_6wpe_UV$x, ymin=pred_lat_growth_2mo_6wpe_UV$Q2.5, ymax=pred_lat_growth_2mo_6wpe_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_lat_growth_2mo_6wpe_PAR$x, y=pred_lat_growth_2mo_6wpe_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_lat_growth_2mo_6wpe_UV$x, y=pred_lat_growth_2mo_6wpe_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = growth_2mo_6wpe_PAR_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = growth_2mo_6wpe_UV_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(),
              subtitle="d)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 30), breaks = c(0, 10, 20, 30), labels = c(0, 1000, 2000, 3000)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_growth_2mo_6wpe_all <- p.all
plot_lat_growth_2mo_6wpe_all
```


#### Coral colour score
```{r}
load("2mo/2018.03_AM_HFO_2mo_CS_14d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_CS_0d_data.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen", "PAR_t0" = "gray75", "UVR_t0" = "gray75", "Holding tank" = "orchid3")) + theme_light() # (add in if plotting t0 values)

#Add in the below if plotting t0 values as comparison
p.all= p.all+ geom_point(data = CS_0d_PAR_data, aes(x = raw.x, y = CS, colour=factor(light), alpha = 0.3), size = 1.6, position=position_jitter(width = .035, height=0.03), shape = 16)
p.all= p.all+ geom_point(data = CS_0d_UV_data, aes(x = raw.x, y = CS, colour= factor(light), alpha = 0.3), size = 1.9, position=position_jitter(width = .035, height=0.03), shape = 17)

#Add in data
p.all= p.all+ geom_point(data = CS_14d_PAR_data, aes(x = raw.x, y = CS, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .035, height=0.03))
p.all= p.all+ geom_point(data = CS_14d_UV_data, aes(x = raw.x, y = CS, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .035, height=0.03))


#Add in the below if plottnig husbandry control/holding tank values as a reference
p.all= p.all+ geom_point(data = CS_0d_HT_data, aes(x = raw.x, y = CS, colour=factor(light), alpha = 0.3), size = 1.6, position=position_jitter(width = .035, height=0.03), shape = 18)
p.all= p.all+ geom_point(data = CS_14d_HT_data, aes(x = raw.x, y = CS, colour= factor(light), alpha = 0.3), size = 1.9, position=position_jitter(width = .035, height=0.03), shape = 18)


p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Coral~colour~score), #"14 day"~coral~colour~score
              subtitle="a)")
p.all= p.all+ scale_y_continuous(limits = c(-0.03, 7)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue", "gray75", "gray75")) # (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_CS_14d_all <- p.all
plot_CS_14d_all
```

#### Maximum quantum yield
```{r}
load("2mo/2018.03_AM_HFO_2mo_MQY_14d_data.RData")
load("2mo/2018.03_AM_HFO_2mo_MQY_0d_data.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen", "PAR_t0" = "gray75", "UVR_t0" = "gray75", "Holding tank" = "orchid3")) + theme_light() 


#Add in the below if plotting t0 values as comparison
p.all= p.all+ geom_point(data = MQY_0d_PAR_data, aes(x = raw.x, y = yield, colour=factor(light), alpha = 0.3), size = 1.6, position=position_jitter(width = .025, height=0.03), shape = 16)
p.all= p.all+ geom_point(data = MQY_0d_UV_data, aes(x = raw.x, y = yield, colour= factor(light), alpha = 0.3), size = 1.9, position=position_jitter(width = .025, height=0.03), shape = 17)

#Add in data
p.all= p.all+ geom_point(data = MQY_14d_PAR_data, aes(x = raw.x, y = yield, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = MQY_14d_UV_data, aes(x = raw.x, y = yield, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))


#Add in the below if plottnig husbandry control/holding tank values as a reference
p.all= p.all+ geom_point(data = MQY_14d_HT_data, aes(x = raw.x, y = yield, colour= factor(light), alpha = 0.3), size = 1.9, position=position_jitter(width = .035, height=0.03), shape = 18)


p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Maximum~quantum~yield), #Maximum~quantum~yield
              subtitle="b)")
p.all= p.all+ scale_y_continuous(limits = c(-0.03, 0.7)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue", "gray75", "gray75")) # (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_MQY_14dall <- p.all
plot_MQY_14dall
```



