---
title: "Ch 2_results&layouts_ECLC50"
author: "Mikaela Nordborg"
date: "08/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#For model fitting, evaluation & extraction of results
library(readr)
library(tidyr)
library(dplyr)
require(tidyverse)
library(brms)
library(bayesnec) #install from CRAN in the first instance, for intermediate updates use devtools::install_github("open-AIMS/bayesnec")
library(beepr)

inv.log10 <- function(x){10^x}


#For plotting
library(ggplot2)
library(scales)
library(tidybayes)
library(ggdist)

#For creating layouts & exports
library(ggpubr) #devtools::install_github("kassambara/ggpubr")
```


#EC/LC50 comparison plots

## 1 week post-settlement

### End of exposure (7d)
#### Survival
```{r}
load("2018.01_AM_HFO_1wo_surv_7d_posterior_comp_EC50.RData")

p.comp.EC50 = ggplot(comp_surv_1wo_7d_EC50$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.EC50 = p.comp.EC50 + stat_pointinterval(aes(y = 0.00, x = value, group=model),.width = c(.66, .95), size=0.5)+
  theme_light()

p.comp.EC50 = p.comp.EC50 + scale_fill_manual( values = c("seagreen", "steelblue")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p.comp.EC50 = p.comp.EC50 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50 = p.comp.EC50 + scale_y_continuous(name ="Posterior probability density") 
p.comp.EC50 = p.comp.EC50 + scale_x_continuous(limits = c(-1.02, 2.1), breaks = c(-1, 0, 1, 2), labels = c(0, 1, 10, 100)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.EC50 = p.comp.EC50 + labs(x=expression(), #EC50~(μg~"L"^{-1})
               subtitle="b)")

p.comp.EC50= p.comp.EC50+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 9.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.EC50= p.comp.EC50+ annotate("text", label = "UVR < PAR = 29.21%", x = 0.55, y = 7.86, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename & show plot
comp.plot_surv_1wo_7d_EC50 <- p.comp.EC50
comp.plot_surv_1wo_7d_EC50
```



## 2 months post-settlement
### Part-way through exposure (9d)
#### Survival
```{r}
load("2018.03_AM_HFO_2mo_surv_9d_posterior_comp_EC50.RData")

p.comp.EC50 = ggplot(comp_surv_2mo_9dEC50$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.EC50 = p.comp.EC50 + stat_pointinterval(aes(y = 0.00, x = value, group=model),.width = c(.66, .95), size=0.5)+
  theme_light()

p.comp.EC50 = p.comp.EC50 + scale_fill_manual( values = c("seagreen", "steelblue")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p.comp.EC50 = p.comp.EC50 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50 = p.comp.EC50 + scale_y_continuous(name ="Posterior probability density") 
p.comp.EC50 = p.comp.EC50 + scale_x_continuous(limits = c(-1.02, 2.5), breaks = c(-1, 0, 1, 2), labels = c(0, 1, 10, 100)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.EC50 = p.comp.EC50 + labs(x=expression(), #EC50~(μg~"L"^{-1})
               subtitle="b)")

p.comp.EC50= p.comp.EC50+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 9.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.EC50= p.comp.EC50+ annotate("text", label = "UVR < PAR = 100%", x = 0.55, y = 7.86, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename & show plot
comp.plot_surv_2mo_9d_EC50 <- p.comp.EC50
comp.plot_surv_2mo_9d_EC50
```

#### Relative growth
```{r}
load("2018.03_AM_HFO_2mo_growth_9d_posterior_comp_EC50.RData")

p.comp.EC50 = ggplot(comp_growth_2mo_9dEC50$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.EC50 = p.comp.EC50 + stat_pointinterval(aes(y = 0.00, x = value, group=model),.width = c(.66, .95), size=0.5)+
  theme_light()

p.comp.EC50 = p.comp.EC50 + scale_fill_manual( values = c("seagreen", "steelblue")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p.comp.EC50 = p.comp.EC50 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50 = p.comp.EC50 + scale_y_continuous(name ="Posterior probability density") 
p.comp.EC50 = p.comp.EC50 + scale_x_continuous(limits = c(-1.02, 2.1), breaks = c(-1, 0, 1, 2), labels = c(0, 1, 10, 100)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.EC50 = p.comp.EC50 + labs(x=expression(), #EC50~(μg~"L"^{-1})
               subtitle="b)")

p.comp.EC50= p.comp.EC50+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 4.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.EC50= p.comp.EC50+ annotate("text", label = "UVR < PAR = 9.40%", x = 0.55, y = 3.89, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename & show plot
comp.plot_growth_2mo_9d_EC50 <- p.comp.EC50
comp.plot_growth_2mo_9d_EC50
```

#### Coral colour score
NA



### End of exposure (14d)
#### Survival
```{r}
load("2018.03_AM_HFO_2mo_surv_14d_posterior_comp_EC50.RData")

p.comp.EC50 = ggplot(comp_surv_2mo_14dEC50$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.EC50 = p.comp.EC50 + stat_pointinterval(aes(y = 0.00, x = value, group=model),.width = c(.66, .95), size=0.5)+
  theme_light()

p.comp.EC50 = p.comp.EC50 + scale_fill_manual( values = c("seagreen", "steelblue")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p.comp.EC50 = p.comp.EC50 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50 = p.comp.EC50 + scale_y_continuous(name ="Posterior probability density") 
p.comp.EC50 = p.comp.EC50 + scale_x_continuous(limits = c(-1.02, 2.7), breaks = c(-1, 0, 1, 2), labels = c(0, 1, 10, 100)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.EC50 = p.comp.EC50 + labs(x=expression(), #EC50~(μg~"L"^{-1})
               subtitle="b)")

p.comp.EC50= p.comp.EC50+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 9.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.EC50= p.comp.EC50+ annotate("text", label = "UVR < PAR = 89.7%", x = 0.55, y = 7.86, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename & show plot
comp.plot_surv_2mo_14d_EC50 <- p.comp.EC50
comp.plot_surv_2mo_14d_EC50
```

#### Relative growth
```{r}
load("2018.03_AM_HFO_2mo_growth_14d_posterior_comp_EC50.RData")

p.comp.EC50 = ggplot(comp_growth_2mo_14dEC50$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.EC50 = p.comp.EC50 + stat_pointinterval(aes(y = 0.00, x = value, group=model),.width = c(.66, .95), size=0.5)+
  theme_light()

p.comp.EC50 = p.comp.EC50 + scale_fill_manual( values = c("seagreen", "steelblue")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p.comp.EC50 = p.comp.EC50 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50 = p.comp.EC50 + scale_y_continuous(name ="Posterior probability density") 
p.comp.EC50 = p.comp.EC50 + scale_x_continuous(limits = c(-1.02, 2.1), breaks = c(-1, 0, 1, 2), labels = c(0, 1, 10, 100)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.EC50 = p.comp.EC50 + labs(x=expression(), #EC50~(μg~"L"^{-1})
               subtitle="b)")

p.comp.EC50= p.comp.EC50+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 9.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.EC50= p.comp.EC50+ annotate("text", label = "UVR < PAR = 33.20%", x = 0.55, y = 7.86, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename & show plot
comp.plot_growth_2mo_14d_EC50 <- p.comp.EC50
comp.plot_growth_2mo_14d_EC50
```

#### Coral colour score
NA

#### Maximum quantum yield
NA



### Latent effects
#### Survival 1 week post-exposure
```{r}
load("2018.03_AM_HFO_2mo_lat_surv_1wpe_posterior_comp_EC50.RData")

p.comp.EC50 = ggplot(comp_lat_surv_2mo_1wpe_EC50$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.EC50 = p.comp.EC50 + stat_pointinterval(aes(y = 0.00, x = value, group=model),.width = c(.66, .95), size=0.5)+
  theme_light()

p.comp.EC50 = p.comp.EC50 + scale_fill_manual( values = c("seagreen", "steelblue")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p.comp.EC50 = p.comp.EC50 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50 = p.comp.EC50 + scale_y_continuous(name ="Posterior probability density") 
p.comp.EC50 = p.comp.EC50 + scale_x_continuous(limits = c(-1.02, 2.5), breaks = c(-1, 0, 1, 2), labels = c(0, 1, 10, 100)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.EC50 = p.comp.EC50 + labs(x=expression(), #EC50~(μg~"L"^{-1})
               subtitle="b)")

p.comp.EC50= p.comp.EC50+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 9.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.EC50= p.comp.EC50+ annotate("text", label = "UVR < PAR = 85.46%", x = 0.55, y = 7.86, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename & show plot
comp.plot_lat_surv_2mo_1wpe_EC50 <- p.comp.EC50
comp.plot_lat_surv_2mo_1wpe_EC50
```

#### Growth 1 week post-exposure
```{r}
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_posterior_comp_EC50.RData")

p.comp.EC50 = ggplot(comp_lat_growth_2mo_1wpe_EC50$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.EC50 = p.comp.EC50 + stat_pointinterval(aes(y = 0.00, x = value, group=model),.width = c(.66, .95), size=0.5)+
  theme_light()

p.comp.EC50 = p.comp.EC50 + scale_fill_manual( values = c("seagreen", "steelblue")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p.comp.EC50 = p.comp.EC50 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50 = p.comp.EC50 + scale_y_continuous(name ="Posterior probability density") 
p.comp.EC50 = p.comp.EC50 + scale_x_continuous(limits = c(-1.02, 2.1), breaks = c(-1, 0, 1, 2), labels = c(0, 1, 10, 100)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.EC50 = p.comp.EC50 + labs(x=expression(), #EC50~(μg~"L"^{-1})
               subtitle="b)")

p.comp.EC50= p.comp.EC50+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 9.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.EC50= p.comp.EC50+ annotate("text", label = "UVR < PAR = 47.20%%", x = 0.55, y = 7.86, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename & show plot
comp.plot_lat_growth_2mo_1wpe_EC50 <- p.comp.EC50
comp.plot_lat_growth_2mo_1wpe_EC50
```

#### Vertical growth 2 weeks post-exposure

