---
title: "2018.03_AM_HFO_2mo_lat_growth_1wpe"
author: "Mikaela Nordborg"
date: "24/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#For model fitting, evaluation & extraction of results
library(readr)
library(tidyr)
library(dplyr)
require(tidyverse)
library(brms)
library(bayesnec) #devtools::install_github("open-AIMS/bayesnec")
library(beepr)

inv.log10 <- function(x){10^x}

#select usingcmdstanr instead of rtools
require(cmdstanr)
set_cmdstan_path("C:/cmdstan")
options(brms.backend = "cmdstanr")

#For plotting
library(ggplot2)
library(scales)
library(tidybayes)

#For creating layouts & exports
library(ggpubr) #devtools::install_github("kassambara/ggpubr")
```

# Background

Relative growth ((area_assessment-area_start)/area_start) of 2 month old Acropora millepora corals exposed to the water accommodated fractions (WAF) of heavy fuel oil in the presence or absence of ultraviolet radiation (UV). All samples where tissue loss occurred relative to the start of exposure were adjusted to 0. 

Column headings used:

  date                        = date of assessment/imaging
  endpoint                    = outlines the endpoint assessed for the dataset
  exp_time                    = exposure time (days)
  light                       = light treatment corals were exposed under; visible light in the absence (PAR) or presence (UVR) of UV radiation
  nom.x                       = nominal treatment concentration (% WAF)
  raw.x                       = time-averaged, measured treatment concentration (ug TAH/L)
  rep                         = replicate chamber.ID for the treatment combination (1-7)
  chamber.ID                  = exposure chamber used (1-79)
  tile.ID                     = tile number (1-249)
  org.ID                      = identifier for individual corals within a replicate (1-4)
  recovery_tray               = tray corals were placed in during post-exposure recovery(1-10). Use to identify the image file analysed for post-exposure endpoints
  tray_position               = photograph position in tray (1-6 or 1-4). Use to identify the image file analysed for post-exposure endpoints.
  tile_position               = position of individual glass tiles within the section of tray that each image file is showing. Use to identify the image file analysed for post-exposure endpoints
  recovery_ROI                = ROi number assigned to each coral still alive at the end of exposure. Use to identify individual corals measured in image files analysed.
  live_area                   = total area of live tissue measured from scaled image files (mm^2)
  growth_vs_mort              = initial result of relative growth calculation which includes both tissue area increases and decreases
  growth                      = proportional increase in live tissue area since start of exposure (>0).
  growth_rate                 = proportional increase in live tissue area per day since start of exposure (>0; increase/day).
  comments                    = comments relating to individual data points
  use_in_model                = specifies which data points should be included in statistical analysis
  reason_for_exclusion        = specifies the reason for exclusion form statistical analysis (f applicable)
  use_in_plot                 = specifies whether data should be used in results graphics or not
  reason_for_exclusion_plot   = specifies why data point should not be included in result graphics



# Import and prepare data for analysis
```{r}
#all models  - no x transformation
juv_lat_growth_data <- readr::read_csv("csv files/2018.03_AM_HFO_2mo_latent_growth.csv") 

#Check the range of concentration (x) values for the data
unique(juv_lat_growth_data$raw.x)
```

## Data wrangling/clean-up
```{r}
juv_lat_growth_data <- readr::read_csv("csv files/2018.03_AM_HFO_2mo_latent_growth.csv") %>% 
  data.frame() %>% dplyr::mutate(light=as.factor(as.character(light)),
                                 exp_time=as.factor(as.character(exp_time)),
                                 nom.x=as.character(nom.x),
                                 raw.x=as.numeric(as.character(raw.x)),
                                 raw.x=ifelse(raw.x==0, 0.1, raw.x), # deal with 0 concentration values
                                 rep=as.factor(as.numeric(rep)),
                                 chamber.ID=as.factor(as.numeric(chamber.ID)),
                                 tile.ID=as.factor(as.character(tile.ID)),
                                 org.ID=as.factor(as.numeric(org.ID)),
                                 live_area=as.numeric(as.character(live_area)),
                                 growth_vs_mort=as.numeric(as.character(growth_vs_mort)),
                                 growth=as.numeric(growth),
                                 log.x=log10(raw.x)) # create log values (doesn't really matter if it's log or log10() unless there's a difference in the scaling of the x-data)
                                 
str(juv_lat_growth_data)
head(juv_lat_growth_data)
tail(juv_lat_growth_data)
```


## Filter data
```{r}
#filter for exposure time
growth_2mo_1wpe_data <-juv_lat_growth_data %>% 
  dplyr::filter(exp_time=="1 week post-exposure") 

#filter for whether replicates should be included in model fitting
growth_2mo_1wpe_data <- growth_2mo_1wpe_data %>% 
  dplyr::filter(use_in_model=="Yes")



#filter for light treatment
growth_2mo_1wpe_PAR_data <- growth_2mo_1wpe_data %>% 
  dplyr::filter(light=="PAR")
  
growth_2mo_1wpe_UV_data <- growth_2mo_1wpe_data %>% 
  dplyr::filter(light=="UVR")

#check that filtering worked
View(growth_2mo_1wpe_PAR_data)
View(growth_2mo_1wpe_UV_data)
```


### Save filtered data as an RData object
```{r}
save(growth_2mo_1wpe_PAR_data, growth_2mo_1wpe_UV_data, file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_data.RData")
```



# PAR/-UV data

## Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_data.RData")

unique(growth_2mo_1wpe_PAR_data$raw.x)
par(mfrow=c(2,1))
hist(growth_2mo_1wpe_PAR_data$raw.x)
hist(growth_2mo_1wpe_PAR_data$growth)
par(mfrow=c(1,1))
plot(growth_2mo_1wpe_PAR_data$log.x, growth_2mo_1wpe_PAR_data$growth) #use this to get an initial visual idea of priors to use (if setting priors manually)
```




## Fit a model-averaged NEC-model (MANEC) using the betabinomial distribution
```{r, eval=FALSE}
load(file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_data.RData")


out_lat_growth_2mo_1wpe_PAR_all <- bayesnec::bnec(growth ~ crf(log.x, model = "decline"),
                                     data = growth_2mo_1wpe_PAR_data, family = Gamma(link = "identity"))

save(out_lat_growth_2mo_1wpe_PAR_all, file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_PAR_modfit_all.RData")
beepr::beep("mario")
```



## Check model fit
Check if any candidate models failed the rHat test
```{r}
load(file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_PAR_modfit_all.RData")
rhat(out_lat_growth_2mo_1wpe_PAR_all, rhat_cutoff = 1.03)
```


Check model summary
```{r}
out_lat_growth_2mo_1wpe_PAR_all$mod_stats
summary(out_lat_growth_2mo_1wpe_PAR_all)
```


Check the overall MANEC fit
```{r}
plot(out_lat_growth_2mo_1wpe_PAR_all, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
```

Check chain mixing, priors and the fit of the individual candidate models
```{r}
check_chains(out_lat_growth_2mo_1wpe_PAR_all, filename = "2018.03_AM_HFO_2mo_lat_growth_1wpe_PAR_modfit_chains")

check_priors(out_lat_growth_2mo_1wpe_PAR_all, filename = "2018.03_AM_HFO_2mo_lat_growth_1wpe_PAR_modfit_priors")

pdf("2018.03_AM_HFO_2mo_lat_growth_1wpe_PAR_modfit_fitplots.pdf")
plot(out_lat_growth_2mo_1wpe_PAR_all, all_models = TRUE, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
dev.off()
```

  *Any evidence of poor chain mixing or convergence issues?*
      - No
 
  *Any indications that the prior distributions were influencing the posterior distributions more than the observed data?*
      - No

  *Should any of the candidate models be excluded based on the fit relative to the raw data?*
      - ecxexp

Drop inappropriate models and models with non-convergence or very poor chain mixing (if required)
```{r}
out_lat_growth_2mo_1wpe_PAR_mod <- amend(out_lat_growth_2mo_1wpe_PAR_all, drop = c("ecxexp"))

save(out_lat_growth_2mo_1wpe_PAR_all, out_lat_growth_2mo_1wpe_PAR_mod, file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_PAR_modfit_all.RData")
```


Compare the MANEC containing all OD candidate models to the amended MANEC
```{r}
plot(out_lat_growth_2mo_1wpe_PAR_all, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
plot(out_lat_growth_2mo_1wpe_PAR_mod, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```



## Select final MANEC to use

Rename model output for selected MANEC
```{r}
out_lat_growth_2mo_1wpe_PAR <- out_lat_growth_2mo_1wpe_PAR_mod
```


Extract the NEC-model subset for use in extraction of NEC and comparisons of posterior distributions
```{r}
out_lat_growth_2mo_1wpe_PAR_NEC <- pull_out(out_lat_growth_2mo_1wpe_PAR, model = c("nec"))
```


```{r}
plot(out_lat_growth_2mo_1wpe_PAR_NEC, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
```


Save the output for the selected models
```{r}
save(out_lat_growth_2mo_1wpe_PAR, out_lat_growth_2mo_1wpe_PAR_NEC, file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_PAR_modfits_final.RData")
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_PAR_modfits_final.RData")
```



## Extract results

Extract NEC, EC10 and EC50 (with 95% credible intervals) from posterior and backtransform if required
```{r}
NEC_lat_growth_2mo_1wpe_PAR <- out_lat_growth_2mo_1wpe_PAR_NEC$w_nec
NEC_lat_growth_2mo_1wpe_PAR <- 10^NEC_lat_growth_2mo_1wpe_PAR #if using log10(raw.x)
#NEC_lat_growth_2mo_1wpe_PAR <- exp(NEC_lat_growth_2mo_1wpe_PAR) #if using log(raw.x))
NEC_lat_growth_2mo_1wpe_PAR
```

```{r}
EC10_lat_growth_2mo_1wpe_PAR <- ecx(out_lat_growth_2mo_1wpe_PAR, ecx_val = 10, type = "absolute")
EC10_lat_growth_2mo_1wpe_PAR <- 10^EC10_lat_growth_2mo_1wpe_PAR #if using log10(raw.x)
#EC10_lat_growth_2mo_1wpe_PAR <- exp(EC10_lat_growth_2mo_1wpe_PAR) #if using log(raw.x))
EC10_lat_growth_2mo_1wpe_PAR
```

```{r}
EC50_lat_growth_2mo_1wpe_PAR <- ecx(out_lat_growth_2mo_1wpe_PAR, ecx_val = 50, type = "absolute")
EC50_lat_growth_2mo_1wpe_PAR <- 10^EC50_lat_growth_2mo_1wpe_PAR #if using log10(raw.x)
#EC50_lat_growth_2mo_1wpe_PAR <- exp(EC50_lat_growth_2mo_1wpe_PAR) #if using log(raw.x))
EC50_lat_growth_2mo_1wpe_PAR
```


# UV/+UV data

## Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_data.RData")

unique(growth_2mo_1wpe_UV_data$raw.x)
par(mfrow=c(2,1))
hist(growth_2mo_1wpe_UV_data$raw.x)
hist(growth_2mo_1wpe_UV_data$growth)
par(mfrow=c(1,1))
plot(growth_2mo_1wpe_UV_data$log.x, growth_2mo_1wpe_UV_data$growth) #use this to get an initial visual idea of priors to use (if setting priors manually)
```


## Fit a model-averaged NEC-model (MANEC) using the betabinomial distribution
```{r, eval=FALSE}
load(file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_data.RData")

out_lat_growth_2mo_1wpe_UV_all <- bayesnec::bnec(growth ~ crf(log.x, model = "decline"),
                                     data = growth_2mo_1wpe_UV_data, family = Gamma(link = "identity"))

save(out_lat_growth_2mo_1wpe_UV_all, file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_UV_modfit_all.RData")
beepr::beep("mario")
```


## Check model fit
Check if any candidate models failed the rHat test
```{r}
load(file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_UV_modfit_all.RData")
rhat(out_lat_growth_2mo_1wpe_UV_all, rhat_cutoff = 1.03)
```



Check model summary
```{r}
out_lat_growth_2mo_1wpe_UV_all$mod_stats
summary(out_lat_growth_2mo_1wpe_UV_all)
```


Check the overall MANEC fit
```{r}
plot(out_lat_growth_2mo_1wpe_UV_all, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
```

Check chain mixing, priors and the fit of the individual candidate models
```{r}
check_chains(out_lat_growth_2mo_1wpe_UV_all, filename = "2018.03_AM_HFO_2mo_lat_growth_1wpe_UV_modfit_chains")

check_priors(out_lat_growth_2mo_1wpe_UV_all, filename = "2018.03_AM_HFO_2mo_lat_growth_1wpe_UV_modfit_priors")

pdf("2018.03_AM_HFO_2mo_lat_growth_1wpe_UV_modfit_fitplots.pdf")
plot(out_lat_growth_2mo_1wpe_UV_all, all_models = TRUE, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
dev.off()
```

  *Any evidence of poor chain mixing or convergence issues?*
      - No
  
  *Any indications that the prior distributions were influencing the posterior distributions more than the observed data?*
      - No

  *Should any of the candidate models be excluded based on the fit relative to the raw data?*
      - ecxexp

Drop inappropriate models and models with non-convergence or very poor chain mixing (if required)
```{r}
out_lat_growth_2mo_1wpe_UV_mod <- amend(out_lat_growth_2mo_1wpe_UV_all, drop = c("ecxexp"))

save(out_lat_growth_2mo_1wpe_UV_all, out_lat_growth_2mo_1wpe_UV_mod, file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_UV_modfit_all.RData")
```


Compare the MANEC containing all candidate models to the amended MANEC
```{r}
plot(out_lat_growth_2mo_1wpe_UV_all, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
plot(out_lat_growth_2mo_1wpe_UV_mod, add_ec10 = FALSE, add_nec = TRUE, lxform = inv.log10) #if modeled on log(raw.x) use: lxform = exp
```



## Select final MANEC to use

Rename model output for selected MANEC
```{r}
out_lat_growth_2mo_1wpe_UV <- out_lat_growth_2mo_1wpe_UV_mod
```


Extract the NEC-model subset for use in extraction of NEC and comparisons of posterior distributions
```{r}
out_lat_growth_2mo_1wpe_UV_NEC <- pull_out(out_lat_growth_2mo_1wpe_UV, model = c("nec"))
```


```{r}
plot(out_lat_growth_2mo_1wpe_UV_NEC, add_nec = TRUE, lxform = inv.log10) #if modelled on log(raw.x) use: lxform = exp
```


Save the output for the selected models
```{r}
save(out_lat_growth_2mo_1wpe_UV, out_lat_growth_2mo_1wpe_UV_NEC, file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_UV_modfits_final.RData")
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_UV_modfits_final.RData")
```



## Extract results

Extract NEC, EC10 and EC50 (with 95% credible intervals) from posterior and backtransform if required
```{r}
NEC_lat_growth_2mo_1wpe_UV <- out_lat_growth_2mo_1wpe_UV_NEC$w_nec
NEC_lat_growth_2mo_1wpe_UV <- 10^NEC_lat_growth_2mo_1wpe_UV #if using log10(raw.x)
#NEC_lat_growth_2mo_1wpe_UV <- exp(NEC_lat_growth_2mo_1wpe_UV) #if using log(raw.x))
NEC_lat_growth_2mo_1wpe_UV
```

```{r}
EC10_lat_growth_2mo_1wpe_UV <- ecx(out_lat_growth_2mo_1wpe_UV, ecx_val = 10, type = "absolute")
EC10_lat_growth_2mo_1wpe_UV <- 10^EC10_lat_growth_2mo_1wpe_UV #if using log10(raw.x)
#EC10_lat_growth_2mo_1wpe_UV <- exp(EC10_lat_growth_2mo_1wpe_UV) #if using log(raw.x))
EC10_lat_growth_2mo_1wpe_UV
```

```{r}
EC50_lat_growth_2mo_1wpe_UV <- ecx(out_lat_growth_2mo_1wpe_UV, ecx_val = 50, type = "absolute")
EC50_lat_growth_2mo_1wpe_UV <- 10^EC50_lat_growth_2mo_1wpe_UV #if using log10(raw.x)
#EC50_lat_growth_2mo_1wpe_UV <- exp(EC50_lat_growth_2mo_1wpe_UV) #if using log(raw.x))
EC50_lat_growth_2mo_1wpe_UV
```



# Comparison of light treatments
## Predict response values

Extract complete posteriors for the fitted values using compare_posterior-function
```{r}
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_PAR_modfits_final.RData")
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_UV_modfits_final.RData")

pred_lat_growth_2mo_1wpe <- compare_posterior(x=list("PAR" = out_lat_growth_2mo_1wpe_PAR, "UVR" = out_lat_growth_2mo_1wpe_UV), comparison = "fitted", precision = 50)

pred_lat_growth_2mo_1wpe_PAR <- pred_lat_growth_2mo_1wpe$posterior_data %>% 
  dplyr::filter(model=="PAR") %>%
  dplyr::filter(x<=(max(growth_2mo_1wpe_PAR_data$log.x)+0.1))

pred_lat_growth_2mo_1wpe_UV <- pred_lat_growth_2mo_1wpe$posterior_data %>% 
  dplyr::filter(model=="UVR") %>%
  dplyr::filter(x<=(max(growth_2mo_1wpe_UV_data$log.x)+0.1))



pred_lat_growth_2mo_1wpe_NEC <- compare_posterior(list("PAR" = out_lat_growth_2mo_1wpe_PAR_NEC, "UVR" = out_lat_growth_2mo_1wpe_UV_NEC), comparison = "fitted", precision = 50)

pred_lat_growth_2mo_1wpe_PAR_NEC <- pred_lat_growth_2mo_1wpe_NEC$posterior_data %>% 
  dplyr::filter(model=="PAR") %>%
  dplyr::filter(x<=(max(growth_2mo_1wpe_PAR_data$log.x)+0.1))

pred_lat_growth_2mo_1wpe_UV_NEC <- pred_lat_growth_2mo_1wpe_NEC$posterior_data %>% 
 dplyr::filter(model=="UVR") %>%
  dplyr::filter(x<=(max(growth_2mo_1wpe_UV_data$log.x)+0.1))


save(pred_lat_growth_2mo_1wpe, pred_lat_growth_2mo_1wpe_PAR, pred_lat_growth_2mo_1wpe_UV, pred_lat_growth_2mo_1wpe_PAR_NEC, pred_lat_growth_2mo_1wpe_UV_NEC, file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_predvals.RData") # pred_lat_growth_2mo_1wpe_NEC, pred_lat_growth_2mo_1wpe_PAR_NEC, pred_lat_growth_2mo_1wpe_UV_NEC <- add these back in once UV-section is working

load("2018.03_AM_HFO_2mo_lat_growth_1wpe_predvals.RData")
str(pred_lat_growth_2mo_1wpe_PAR)
str(pred_lat_growth_2mo_1wpe_UV)
```


## Determine the highest probability that there is a difference
The highest probability that the two light treatments are different (at any tested x-value) is:
```{r}
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_predvals.RData")

diff_lat_growth_2mo_1wpe <- max(pred_lat_growth_2mo_1wpe$prob_diff$prob)
diff_lat_growth_2mo_1wpe
```



## EC50

Perform comparison of posterior distributions for partial growth EC50
```{r}
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_PAR_modfits_final.RData")
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_UV_modfits_final.RData")

comp_lat_growth_2mo_1wpe_EC50 <- compare_posterior(x=list("PAR" = out_lat_growth_2mo_1wpe_PAR, "UVR" = out_lat_growth_2mo_1wpe_UV), comparison = "ecx", ecx_val = 50)
save(comp_lat_growth_2mo_1wpe_EC50, file = "2018.03_AM_HFO_2mo_lat_growth_1wpe_posterior_comp_EC50.RData")
comp_lat_growth_2mo_1wpe_EC50$prob_diff
```
Table shows the % likelihood that the point estimate calculated (NEC, EC/LC10 or EC/LC50) for model A (in top row) is smaller than the point estimate calculated for model B, C, etc (in left hand column). 

*Is EC50 +UVR lower than the EC50 -UVR?*
    - No, both EC50s appear to be the same (likelihood of a difference is 47.2%)






# Graphical presentation of results
## Concentration-response relationship and raw data
### Complete subset-MANEC plot


```{r}
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_data.RData")
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_predvals.RData")

p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)


p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_growth_2mo_1wpe_PAR$x, ymin=pred_lat_growth_2mo_1wpe_PAR$Q2.5, ymax=pred_lat_growth_2mo_1wpe_PAR$Q97.5, fill="seagreen"),  alpha=0.3)
#p.all= p.all+  scale_fill_manual(values=c("seagreen", "steelblue"))
p.all= p.all+ geom_ribbon(aes(x=10^pred_lat_growth_2mo_1wpe_UV$x, ymin=pred_lat_growth_2mo_1wpe_UV$Q2.5, ymax=pred_lat_growth_2mo_1wpe_UV$Q97.5, fill="steelblue",  alpha=0.3))
#p.all= p.all+  scale_fill_manual(values="steelblue")


p.all= p.all+ geom_line(aes(x=10^pred_lat_growth_2mo_1wpe_PAR$x, y=pred_lat_growth_2mo_1wpe_PAR$Estimate), color = 'grey30', size=0.5)
p.all= p.all+ geom_line(aes(x=10^pred_lat_growth_2mo_1wpe_UV$x, y=pred_lat_growth_2mo_1wpe_UV$Estimate), color = 'grey30', size=0.5)


p.all= p.all+ geom_point(data = growth_2mo_1wpe_PAR_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p.all= p.all+ geom_point(data = growth_2mo_1wpe_UV_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))


p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(growthival~("%")),
              subtitle="a)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.7), breaks = c(0, 0.5, 1.0, 1.5), labels = c(0, 50, 100, 150)) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.09, 500), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_growth_2mo_1wpe_all <- p.all
plot_lat_growth_2mo_1wpe_all
```


### NEC subset-MANEC plot

```{r}
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_data.RData")
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_predvals.RData")

p_NEC= ggplot()
p_NEC= p_NEC+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light()


p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_lat_growth_2mo_1wpe_PAR_NEC$x, ymin=pred_lat_growth_2mo_1wpe_PAR_NEC$Q2.5, ymax=pred_lat_growth_2mo_1wpe_PAR_NEC$Q97.5, fill="seagreen"),  alpha=0.3) #Seagreen HEX code: #2e8b57
#p_NEC= p_NEC+  scale_fill_manual(values=c("seagreen", "steelblue"))
p_NEC= p_NEC+  geom_ribbon(aes(x=10^pred_lat_growth_2mo_1wpe_UV_NEC$x, ymin=pred_lat_growth_2mo_1wpe_UV_NEC$Q2.5, ymax=pred_lat_growth_2mo_1wpe_UV_NEC$Q97.5,fill="steelblue",  alpha=0.3))
#p_NEC= p_NEC+  scale_fill_manual(values="steelblue")


p_NEC= p_NEC+ geom_line(aes(x=10^pred_lat_growth_2mo_1wpe_PAR_NEC$x, y=pred_lat_growth_2mo_1wpe_PAR_NEC$Estimate), color = 'grey30', size=0.5)
p_NEC= p_NEC+ geom_line(aes(x=10^pred_lat_growth_2mo_1wpe_UV_NEC$x, y=pred_lat_growth_2mo_1wpe_UV_NEC$Estimate), color = 'grey30', size=0.5)


p_NEC= p_NEC+ geom_point(data = growth_2mo_1wpe_PAR_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
p_NEC= p_NEC+ geom_point(data = growth_2mo_1wpe_UV_data, aes(x = raw.x, y = growth, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))


p_NEC = p_NEC+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})),
              y=expression(growthival~("%")),
              subtitle="a)")
p_NEC= p_NEC+ scale_y_continuous( limits = c(-0.03,  1.7), breaks = c(0, 0.5, 1.0, 1.5), labels = c(0, 50, 100, 150)) 
p_NEC= p_NEC+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p_NEC= p_NEC+ scale_fill_manual(values = c("seagreen", "steelblue"))
p_NEC= p_NEC+ theme(legend.position="none")
# p_NEC = p_NEC  + theme(legend.position = c(0.9, 0.9))
p_NEC= p_NEC+ scale_x_continuous(limits = c(0.09, 500), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p_NEC= p_NEC+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_growth_2mo_1wpe_NEC <- p_NEC
plot_lat_growth_2mo_1wpe_NEC
```


## Comparison of light treatments across concentrations


### Probability of a difference between light treatments plot
Plot the probability of a difference between the UV and PAR light treatments across the treatment concentrations tested
```{r}
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_predvals.RData")

pred_lat_growth_2mo_1wpe$prob_diff$inv.x <- 10^pred_lat_growth_2mo_1wpe$prob_diff$x

p.comp.prob= ggplot(pred_lat_growth_2mo_1wpe$prob_diff) +
                geom_line(aes(x=inv.x, prob, color="grey"), size=0.8)

p.comp.prob= p.comp.prob + scale_color_manual(values = c("grey")) +
                theme_light() +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80")) +
                theme(legend.position="none") 
    
p.comp.prob= p.comp.prob + scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1.0), labels = c(0, 25, 50, 75, 100)) +
                scale_x_continuous(limits = c(0.09, 500), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 1000)) +
                labs(x=expression(Treatment~concentration~(μg~TAH~"L"^{-1})),
                      y=expression(Probability~that~UVR~affected~toxicity~("%")),
                      subtitle="a)")

plot_lat_growth_2mo_1wpe_diff.prob <- p.comp.prob
plot_lat_growth_2mo_1wpe_diff.prob
```

    If solid line (probability) is higher than 95%/0.95 = UVR significantly increased toxicity at that treatment concentration

### Posterior differences plot
Plot the posterior difference estimate for the UV and PAR light treatments across the treatment concentrations tested
```{r}
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_predvals.RData")

pred_lat_growth_2mo_1wpe$diff_data$inv.x <- 10^pred_lat_growth_2mo_1wpe$diff_data$x

p.comp.diff = ggplot(pred_lat_growth_2mo_1wpe$diff_data) +
  geom_ribbon(aes(x=inv.x, ymin=diff.Q2.5, ymax=diff.Q97.5, fill = 'grey'), alpha=0.4) +
  geom_line(aes(x=inv.x, diff.Estimate, color="grey"), size=0.8) +
  geom_hline(yintercept = 0, color = "steelblue3", lty = 2, size=0.75)


p.comp.diff= p.comp.diff + scale_fill_manual( values = c("grey", "steelblue3")) +
                scale_color_manual(values = c("grey", "steelblue3")) 
  
p.comp.diff= p.comp.diff + theme_light() + 
                theme(legend.position="none") +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.diff= p.comp.diff + scale_y_continuous(name = "Posterior differences estimate") 
p.comp.diff= p.comp.diff + scale_x_continuous(limits = c(0.09, 500), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100)) +
              labs(x=expression(Treatment~concentration~(μg~TAH~"L"^{-1})),
                  y=expression(Posterior~difference~estimate),
                  subtitle="a)")

plot_lat_growth_2mo_1wpe_diff.est <- p.comp.diff
plot_lat_growth_2mo_1wpe_diff.est
```

    If credible intervals (shaded grey area) includes 0 (dotted blue line) there is no significant difference between the two models at that treatment concentration.


## EC50 comparison

Create a custom results plot of the EC50 comparison
```{r}
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_posterior_comp_EC50.RData")

p.comp.EC50 = ggplot(comp_lat_growth_2mo_1wpe_EC50$posterior_data, aes(x=value))+geom_density(aes(group=model, color=model, fill=model), alpha=0.4) 
p.comp.EC50 = p.comp.EC50 + stat_pointinterval(aes(y = 0.00, x = value, group=model),.width = c(.66, .95), size=0.5)+
  theme_light()

p.comp.EC50 = p.comp.EC50 + scale_fill_manual( values = c("seagreen", "steelblue")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue", "grey","grey", "grey","grey"))+theme(legend.position="none")
p.comp.EC50 = p.comp.EC50 + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50 = p.comp.EC50 + scale_y_continuous(name ="Posterior probability density") 
p.comp.EC50 = p.comp.EC50 + scale_x_continuous(limits = c(-1.02, 2.1), breaks = c(-1, 0, 1, 2), labels = c(0, 1, 10, 100)) #update breaks+labels to match the scale given by the automatic compare_posterior output
p.comp.EC50 = p.comp.EC50 + labs(x=expression(), #EC50~(μg~"L"^{-1})
               subtitle="b)")

p.comp.EC50= p.comp.EC50+ annotate("text", label = expression(Probability~of~EC[50]~difference), x = 0.55, y = 9.3, size = 2.8, colour = "grey20") #0.8 of the max y-axis limit
p.comp.EC50= p.comp.EC50+ annotate("text", label = "UVR < PAR = 47.20%%", x = 0.55, y = 7.86, size = 2.4, colour = "grey20") #0.906 of the first annotation


#Rename & show plot
comp.plot_lat_growth_2mo_1wpe_EC50 <- p.comp.EC50
comp.plot_lat_growth_2mo_1wpe_EC50
```


Create a custom plot of the EC50 comparisons differences posterior density
```{r}
load("2018.03_AM_HFO_2mo_lat_growth_1wpe_posterior_comp_EC50.RData")

p.comp.EC50.diff = ggplot(comp_lat_growth_2mo_1wpe_EC50$diff_data, aes(x=diff)) +
  geom_density(aes(x=diff, fill = 'grey'), alpha=0.4) + 
  geom_vline(xintercept = 0, color = "red", lty = 2) + 
  theme_light()

p.comp.EC50.diff = p.comp.EC50.diff + scale_fill_manual( values = c("grey", "grey")) +
  scale_color_manual(values = c("grey","grey", "steelblue1","steelblue4", "grey","grey", "grey","grey")) + 
  theme(legend.position="none")
p.comp.EC50.diff = p.comp.EC50.diff + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))

p.comp.EC50.diff = p.comp.EC50.diff + scale_y_continuous(name = "Differences posterior density") 
p.comp.EC50.diff = p.comp.EC50.diff + scale_x_continuous(name = "Standardized effect size") 


#Rename & show plot
comp.plot_lat_growth_2mo_1wpe_EC50.diff <- p.comp.EC50.diff
comp.plot_lat_growth_2mo_1wpe_EC50.diff
```




# Create layouts and export (if required)

Create layout to view result plots side-by-side
```{r}
layout_HFO_2mo_lat_growth_1wpe <- ggarrange(plot_lat_growth_2mo_1wpe_all, comp.plot_lat_growth_2mo_1wpe_EC50, plot_lat_growth_2mo_1wpe_diff.est, plot_lat_growth_2mo_1wpe_NEC,
          ncol = 3, nrow = 2,
          widths = c(0.5, 0.5))
layout_HFO_2mo_lat_growth_1wpe
```
