---
title: "2018.03_AM_HFO_2mo_lat_VG_2wpe"
author: "Mikaela Nordborg"
date: "30/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#For model fitting, evaluation & extraction of results
library(readr)
library(tidyr)
library(dplyr)
require(tidyverse)
library(brms)
library(bayesnec) #devtools::install_github("open-AIMS/bayesnec")
library(beepr)

inv.log10 <- function(x){10^x}

#select usingcmdstanr instead of rtools
require(cmdstanr)
set_cmdstan_path("C:/cmdstan")
options(brms.backend = "cmdstanr")

#For plotting
library(ggplot2)
library(scales)
library(tidybayes)
library(ggdist)

#For creating layouts & exports
library(ggpubr) #devtools::install_github("kassambara/ggpubr")
```

# Background

Vertical growth during post-exposure recovery of 2 month old Acropora millepora corals exposed to the water accommodated fractions (WAF) of heavy fuel oil in the presence or absence of ultraviolet radiation (UV). Assessments performed at 2, 3, 4 and 6 weeks post-exposure (wpe).

Column headings used:

  date                        = date of assessment/imaging
  endpoint                    = outlines the endpoint assessed for the dataset
  exp_time                    = exposure time (days)
  light                       = light treatment corals were exposed under; visible light in the absence (PAR) or presence (UVR) of UV radiation
  nom.x                       = nominal treatment concentration (% WAF)
  raw.x                       = time-averaged, measured treatment concentration (ug TAH/L)
  rep                         = replicate chamber.ID for the treatment combination (1-7)
  chamber.ID                  = exposure chamber used (1-79)
  tile.ID                     = tile number (1-249)
  org.ID                      = identifier for individual corals within a replicate
  recovery_tray               = tray corals were placed in during post-exposure recovery(1-10). Use to identify the image file analysed for post-exposure endpoints
  tray_position               = photograph position in tray (1-6 or 1-4). Use to identify the image file analysed for post-exposure endpoints.
  tile_position               = position of individual glass tiles within the section of tray that each image file is showing. Use to identify the image file analysed for post-exposure endpoints
  recovery_ROI                = ROi number assigned to each coral still alive at the end of exposure. Use to identify individual corals measured in image files analysed.
  VG                 = identifies whether vertical growth was evident for the coral (0 = No vertical growth; 1 = vertical growth observed)
  comments                    = comments relating to individual data points
  use_in_model                = specifies which data points should be included in statistical analysis
  reason_for_exclusion        = specifies the reason for exclusion form statistical analysis (f applicable)
  use_in_plot                 = specifies whether data should be used in results graphics or not
  reason_for_exclusion_plot   = specifies why data point should not be included in result graphics



# Import and prepare data for analysis
```{r}
#all models  - no x transformation
juv_lat_VG_data <- readr::read_csv("csv files/2018.03_AM_HFO_2mo_latent_VG.csv") 

#Check the range of concentration (x) values for the data
unique(juv_lat_VG_data$raw.x)
```

## Data wrangling/clean-up
```{r}
juv_lat_VG_data <- readr::read_csv("csv files/2018.03_AM_HFO_2mo_latent_VG.csv") %>% 
  data.frame() %>% dplyr::mutate(light=as.factor(as.character(light)),
                                 exp_time=as.factor(as.character(exp_time)),
                                 nom.x=as.character(nom.x),
                                 raw.x=as.numeric(as.character(raw.x)),
                                 raw.x=ifelse(raw.x==0, 0.1, raw.x), # deal with 0 concentration values
                                 rep=as.factor(as.numeric(rep)),
                                 chamber.ID=as.factor(as.numeric(chamber.ID)),
                                 tile.ID=as.factor(as.character(tile.ID)),
                                 org.ID=as.factor(as.numeric(org.ID)),
                                 VG=as.integer(VG),
                                 log.x=log10(raw.x), # create log values (doesn't really matter if it's log or log10() unless there's a difference in the scaling of the x-data)
                                 tot=as.integer(1)) #to account for the 5% variability in repeat area measurements
str(juv_lat_VG_data)
head(juv_lat_VG_data)
tail(juv_lat_VG_data)
```


## Filter data
```{r}
#filter for exposure time
VG_2mo_2wpe_data <-juv_lat_VG_data %>% 
  dplyr::filter(exp_time=="2 weeks post-exposure") 

#filter for whether replicates should be included in model fitting
VG_2mo_2wpe_data <- VG_2mo_2wpe_data %>% 
  dplyr::filter(use_in_model=="Yes")



#filter for light treatment
VG_2mo_2wpe_PAR_data <- VG_2mo_2wpe_data %>% 
  dplyr::filter(light=="PAR")
  
VG_2mo_2wpe_UV_data <- VG_2mo_2wpe_data %>% 
  dplyr::filter(light=="UVR")

#check that filtering worked
View(VG_2mo_2wpe_PAR_data)
View(VG_2mo_2wpe_UV_data)
```


### Save filtered data as an RData object
```{r}
save(VG_2mo_2wpe_PAR_data, VG_2mo_2wpe_UV_data, file = "2018.03_AM_HFO_2mo_lat_VG_2wpe_data.RData")
```



# PAR/-UV data

## Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2018.03_AM_HFO_2mo_lat_VG_2wpe_data.RData")

unique(VG_2mo_2wpe_PAR_data$raw.x)
par(mfrow=c(2,1))
hist(VG_2mo_2wpe_PAR_data$raw.x)
hist(VG_2mo_2wpe_PAR_data$VG)
par(mfrow=c(1,1))
plot(VG_2mo_2wpe_PAR_data$log.x, VG_2mo_2wpe_PAR_data$VG) #use this to get an initial visual idea of priors to use (if setting priors manually)
```


## Fit a model-averaged NEC-model (MANEC) using the betabinomial distribution
```{r, eval=FALSE}
load(file = "2018.03_AM_HFO_2mo_lat_VG_2wpe_data.RData")


out_lat_VG_2mo_2wpe_PAR_all <- bayesnec::bnec(VG|trials(tot) ~ crf(log.x, model = "decline"),
                                     data = VG_2mo_2wpe_PAR_data)
save(out_lat_VG_2mo_2wpe_PAR_all, file = "2018.03_AM_HFO_2mo_lat_VG_2wpe_PAR_modfit_all.RData")

beepr::beep("mario")
```


    - No models could be fitted as no decline in vertical growth with increasing treatment concentration was observed.


# UV/+UV data

## Initial data exploration

Check distribution of response variable and range of treatment concentrations used
```{r}
load(file = "2018.03_AM_HFO_2mo_lat_VG_2wpe_data.RData")

unique(VG_2mo_2wpe_UV_data$raw.x)
par(mfrow=c(2,1))
hist(VG_2mo_2wpe_UV_data$raw.x)
hist(VG_2mo_2wpe_UV_data$VG)
par(mfrow=c(1,1))
plot(VG_2mo_2wpe_UV_data$log.x, VG_2mo_2wpe_UV_data$VG) #use this to get an initial visual idea of priors to use (if setting priors manually)
```





## Fit a model-averaged NEC-model (MANEC) using the betabinomial distribution
```{r, eval=FALSE}
load(file = "2018.03_AM_HFO_2mo_lat_VG_2wpe_data.RData")

out_lat_VG_2mo_2wpe_UV_all <- bayesnec::bnec(VG|trials(tot) ~ crf(log.x, model = "decline"),
                                     data = VG_2mo_2wpe_UV_data)
save(out_lat_VG_2mo_2wpe_UV_all, file = "2018.03_AM_HFO_2mo_lat_VG_2wpe_UV_modfit_all.RData")

beepr::beep("mario")
```


    - No models could be fitted as no decline in vertical growth with increasing treatment concentration was observed.



# Graphical presentation of results
## Concentration-response relationship and raw data
### Complete subset-MANEC plot


```{r}
load("2018.03_AM_HFO_2mo_lat_VG_2wpe_data.RData")


p.all= ggplot()
p.all= p.all+ scale_color_manual(values = c("UVR" = "steelblue", "PAR" = "seagreen")) + theme_light() #, "PAR_t0" = "gray75", "UVR_t0" = "gray75" (add in if plotting t0 values)



p.all= p.all+ stat_dots(data = VG_2mo_2wpe_PAR_data, aes(x = raw.x, y = VG, colour=factor(light), shape = factor(light), alpha = 0.3, side = ifelse(VG == 0, "top", "bottom")), scale = 0.6, position=position_jitter(width = .07, height=0))
p.all= p.all+ stat_dots(data = VG_2mo_2wpe_UV_data, aes(x = raw.x, y = VG, colour=factor(light), shape = factor(light), alpha = 0.3, side = ifelse(VG == 0, "top", "bottom")), scale = 0.6, position=position_jitter(width = .07, height=0))

#p.all= p.all+ geom_point(data = VG_2mo_2wpe_PAR_data, aes(x = raw.x, y = VG, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2, position=position_jitter(width = .025, height=0.03))
#p.all= p.all+ geom_point(data = VG_2mo_2wpe_UV_data, aes(x = raw.x, y = VG, colour=factor(light), shape = factor(light), alpha = 0.3), size = 2.5, position=position_jitter(width = .025, height=0.03))

p.all= p.all+ geom_hline(yintercept = 0.5, color = "grey30", lty = 2, size=0.5)


p.all = p.all+ labs(x=expression(Concentration~(μg~TAH~"L"^{-1})), #Concentration~(μg~TAH~"L"^{-1})
              y=expression(Vertical~growth),
              subtitle="a)")
p.all= p.all+ scale_y_continuous( limits = c(-0.03, 1.05), breaks = c(0, 1.0), labels = c("No", "Yes")) 
p.all= p.all+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), panel.border = element_blank(), axis.line = element_line(colour = "grey80"))
p.all= p.all+ scale_fill_manual(values = c("seagreen", "steelblue")) #, "gray75", "gray75" (add in if plotting t0 values)
p.all= p.all+ theme(legend.position="none")
# p.all = p.all  + theme(legend.position = c(0.9, 0.9))
p.all= p.all+ scale_x_continuous(limits = c(0.08, 400), trans="log10", breaks = c(0.1, 1, 10, 100), labels = c(0, 1, 10, 100))
#p.all= p.all+ facet_wrap(~factor, nrow = 1)


#Rename & show plot
plot_lat_VG_2mo_2wpe_all <- p.all
plot_lat_VG_2mo_2wpe_all
```


