

# Load required packages
```{r}
require(ssdtools)
library(ggplot2)
require(tidyverse)
```

# Load the McGrath et al.(2018) acute CTLBB database (79spp) and perform initial data wrangling
```{r}
pch.vec <- c(17, 2, 15, 1)

data <- read.csv("McGrath2018_acute_CTLBBs.csv") %>%
  data.frame() %>%
  mutate(log.Conc=log..CL.., 
         log.Conc.lw=log.Conc-SE..log..CL...,
         log.Conc.up=log.Conc+SE..log..CL...,         
         Conc=10^log.Conc,
         Conc.lw=10^log.Conc.lw,
         Conc.up=10^log.Conc.up,
         #Species=if_else(Classification=="Fish", "Fish","other"),
         #Species=if_else(Classification=="Microalgae" | Classification=="Aquatic plant" | Classification=="Phytoplankton", "Algae", Species),
         #Species=if_else(str_detect(ï..Species, "Daphnia"), "Daphnids", Species),
         Species=as.factor(Species)) %>%
  arrange(Conc) %>%
  mutate(frac=ppoints(Conc))

  data$pch.vals <- pch.vec[as.numeric(factor(data$Species))]

head(data)
```

# Fit distributions
```{r}
dist <- ssd_fit_dists(data, left = 'Conc', dists = c('lnorm'))
dist
```

```{r}
pred <- predict(dist, nboot = 10000, ci = TRUE)
```

```{r}
write.csv(pred, file = "Ch2_McGrath_model_fit_prediction.csv")
```



# Derive percentile sensitivty values for back-calculated CTLBB values for A. millepora recruits
```{r}
MK.pa <- data.frame(do.call("rbind", list(
  "1wo - Surv_7d" = c(2.2, 1.8, 3.1),
  "1wo - Surv_8dpe" = c(2.4, 2.0, 3.5),
  "1wo - Surv_6wpe" = c(3.1, 2.1, 4.1),
  "1wo - Growth_8dpe" = c(1.8, 1.5, 3.0),
  "1wo - Growth_6wpe" = c(3.1, 1.6, 4.7),
  "1wo - Symb_8dpe" = c(2.3, 1.7, 7.7),
  "2mo - Surv_9d" = c(13.6, NA, NA),
  "2mo - Surv_14d" = c(8.1, 6.4, 10.0),
  "2mo - Surv_1wpe" = c(8.6, 6.5, 12.9), 
  "2mo - Surv_6wpe" = c(9.4, 6.4, 13.0),
  "2mo - Growth_9d" = c(0.4, 0.1, 1.1),
  "2mo - Growth_14d" = c(0.4, 0.2, 1.0),
  "2mo - Growth_1wpe" = c(0.8, 0.2, 3.0),
  "2mo - Growth_4wpe" = c(5.9, 0.8, 5.9)
  )))
colnames(MK.pa) <- c("Conc", "Conc.lw", "Conc.up")
MK.pa$Study <- row.names(MK.pa)
MK.pa <- MK.pa %>%
  mutate(P=signif(plnorm(q=Conc, meanlog=dist$lnorm$estimate["meanlog"], sdlog=dist$lnorm$estimate["sdlog"]) * 100, 2),
         P.lw=signif(plnorm(q=Conc.lw, meanlog=dist$lnorm$estimate["meanlog"], sdlog=dist$lnorm$estimate["sdlog"]) * 100, 2),
         P.up=signif(plnorm(q=Conc.up, meanlog=dist$lnorm$estimate["meanlog"], sdlog=dist$lnorm$estimate["sdlog"]) * 100, 2))
head(MK.pa)
```


# Export derived percentile values to .csv file
```{r}
write.csv(MK.pa, file="Ch2_Estimated_percent_values_acute.csv")
```


# Derive percentile sensitivity values for CTLBB values published for other scleractinian corals
```{r}
MK.pa <- data.frame(do.call("rbind", list(
  "Acropora cervicornis - 2d survival" = c(180.9, 180.3, 181.5),
  "Porites astreoides - 2d survival" = c(359.9, 283.4, 436.4),
  "Siderastrea siderea - 2d survival" = c(297.4, NA, NA),
  "Stephanoxoenia intersepta - 2d survival" = c(572.2, 566.8, 577.6),
  "Solenastrea bournoni - 2d survival" = c(303.5, NA, NA),
  "Lophelia pertusa - survival" = c(51.6, 49.7, 53.5)
  )))
colnames(MK.pa) <- c("Conc", "Conc.lw", "Conc.up")
MK.pa$Study <- row.names(MK.pa)
MK.pa <- MK.pa %>%
  mutate(P=signif(plnorm(q=Conc, meanlog=dist$lnorm$estimate["meanlog"], sdlog=dist$lnorm$estimate["sdlog"]) * 100, 2),
         P.lw=signif(plnorm(q=Conc.lw, meanlog=dist$lnorm$estimate["meanlog"], sdlog=dist$lnorm$estimate["sdlog"]) * 100, 2),
         P.up=signif(plnorm(q=Conc.up, meanlog=dist$lnorm$estimate["meanlog"], sdlog=dist$lnorm$estimate["sdlog"]) * 100, 2))
```


# Export derived percentile values to .csv file
```{r}
write.csv(MK.pa, file="Ch2_Estimated_percent_values_acute_other_coral.csv")
```




